---
title             : "Factorial structure of the indicators in Big Five Plus Inventory"
shorttitle        : "Factorial structure of the indicators in Big Five Plus Inventory"
author: 
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Ovidius University Campus, Aleea Universității, No. 2, Constanța, Romania"
    email         : "copariuc@gmail.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Data analysis
  - name          : "Gabriela Nicuță"
    affiliation   : "3"
    role:
      - Writing - Systematic review
      - Writing - Data analysis
      - Proofreading
  - name          : "Ticu Constantin"
    affiliation   : "3"
    role:
      - Data provider
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "Ovidius University, Constanta, Romania"
  - id            : "2"
    institution   : "Bucharest University, Bucharest, Romania"
  - id            : "3"
    institution   : "Al. I. Cuza University, Iassy, Romania"
authornote: |
  
  The authors thanks Prof. Dr. Constantin Ticu and the PsihoProfile team for making available over 14000 data used in this analysis.
  
  The data in this paper comes form the Romanian version of BigFive Plus inventory[@BigFive-plus], being collected online through the [PsihoProfile site](http://www.psihoprofile.ro/)
abstract: |
  TO BE DONE AT THE END
keywords          : "BigFive, Confirmatory Factor Analysis, Reliability analysis"
wordcount         : "2348 words in text body, 332 words in reference section"
bibliography      : ["r-references.bib", "Big Five Plus.bib"]
floatsintext      : no
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_doc
header-includes:
  - \usepackage[document]{ragged2e}
---

```{r setup, include = FALSE}
  # Including necessary libraries
  library(papaja); library(knitr); library(kableExtra)
  # Including references file for R libraries
  r_refs("r-references.bib")
```

```{r analysis-preferences}
  # Seed for random number generation
  set.seed(4482)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods

In this paper we aimed to conduct an exploratory study on the **analysis of how the theoretical Big Five model is supported by data**. The volume of the data collected, even if it is very large and gives power to the study, does not constitute a representative sample because no sampling technique was used, but represents the results of tests performed with the Big Five Plus Personality Inventory [@BigFive-plus] during 2015-2020 on the population of Romania. The answers resulted either from an online administration using the [PsihoProfile site](http://www.psihoprofile.ro/), or from the classic administration, pencil-paper, followed by the introduction of the answers in the platform in order to automatically rate and generate assessment's protocols. 

Basically, the manifest variables represent the 240 dichotomous items of the **BigFive Plus Personality Inventory**, the analysis falling into the domain of confirmatory factor analysis using categorical indicators, more precisely dichotomous, and implies a specific approach.

The model does not provide for the existence of indicators loaded in more than one latent trait, each latent factor loading 8 indicators, therefore they will also represent categorical latent variables, because an amplitude of 8 points cannot qualify them as continuous variables.

The latent factors that load the 8 indicators are, in turn, loaded by one of the five Big Five dimensions, resulting in a *second-order factor analysis model* [@Byrne-2010] with uncorrelated second-order factors, which are represented as follows:

+ **Extraversion**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Friendliness*, *Gregariousness*, *Assertiveness*, *Activity level*, *Excitement seeking* and *Cheerfulness*.

+ **Agreeableness**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Trust*, *Morality*, *Altruism*, *Cooperation*, *Modesty* and *Sympathy*.

+ **Neuroticism**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Anxiety*, *Anger*, *Depression*, *Timidity*, *Immoderation* and *Vulnerability*.

+ **Conscientiousness**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Self-efficacy*, *Orderliness*, *Dutifulness*, *Achievement-striving*, *Self-discipline* și *Cautiousness*.

+ **Openness to experience**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Imagination*, *Artistic interests*, *Emotionality*, *Adventurousness*, *Intellect* and *Liberalism*.

## Participants
```{r participants, echo = F, include = F}
 # Computing data
  source("01 - Lotul de cercetare.R")
  # Returning values - n
  n <- gender$output.table[3]
  # Returning values - n by gender
  n.male <- gender$output.table[1]
  n.male.prc <- gender$output.table[4]
  n.female <- gender$output.table[2]
  n.female.prc <- gender$output.table[5]
  # Returning values - n by educational level
  n.st.lic <- studies$output.table[7]
  n.st.lic.prc <- studies$output.table[18]
  n.st.hsc <- studies$output.table[5]
  n.st.hsc.prc <- studies$output.table[16]
  n.st.mst <- studies$output.table[8]
  n.st.mst.prc <- studies$output.table[19]
  n.st.phs <- studies$output.table[6]
  n.st.phs.prc <- studies$output.table[17]
  n.st.art <- studies$output.table[4]
  n.st.art.prc <- studies$output.table[15]
  n.nost <- studies$output.table[10]
  n.nost.prc <- studies$output.table[21]
  # Returning values - n by Type of data gathering
  n.paper <- online$output.table[1]
  n.paper.prc <- online$output.table[4]
  n.online <- online$output.table[2]
  n.online.prc <- online$output.table[5]
```
A total of *`r n`* protocols were collected, administered to a number of *`r n.male` males (`r n.male.prc `%)* and *`r n.female` females (`r n.female.prc`%)* (see Table \@ref(tab:gender)), most of them being *university graduates (n=`r n.st.lic`, representing `r n.st.lic.prc`%)*, followed by *high school graduated (n=`r n.st.hsc`, representing `r n.st.hsc.prc`%)* and the persons with *master's degrees (n=`r n.st.mst`, representing `r n.st.mst.prc`%)*. The research group also contains graduates of *post-secondary schools (n=`r n.st.phs`, representing `r n.st.phs.prc`%)* and graduates of *arts and crafts schools (n=`r n.st.art`, representing `r n.st.art.prc`%)*, the other categories being much less represented. (see Table \@ref(tab:education))

```{r gender, echo=FALSE}
  kable(gender$output.table, format = "latex", digits = 2, booktabs = T,
        caption = "Participants' gender")
```
```{r education, echo=FALSE}
   kable(studies$output.table, format = "latex", digits = 2, booktabs = T,
         caption = "Participants' educational level")
```
We note, however, that a large number of people did not specify the level of education *(n=`r n.nost`, reprezentând `r n.nost.prc`%)*, which will be removed from the analysis that involves the use of this variabile (see Table \@ref(tab:education)).

Regarding the data gathering method, a number of *`r n.paper` protocols* were administered in *paper-pencil form (`r n.paper.prc`%), `r n.online` protocols* being collected directly *online (`r n.online.prc`%)* (see Table \@ref(tab:gather))

```{r gather, echo=FALSE}
   kable(online$output.table, format = "latex", digits = 2, booktabs = T,
         caption = "Type of data gathering")
```
Respondents ranged in age from *min=`r age[2]`* and *max=`r age[6]`* years, with a *median age of `r age[4]`* years *(m=`r age[2]`, sd=`r age[3]`)* (see Table \@ref(tab:age))

```{r age, echo=FALSE}
   kable(age, format = "latex", digits = 2, booktabs = T, row.names = F,
         col.names = c("n", "mean", "sd", "median", "min", "max", "range", "skewness", "kurtosis"),
         caption = "Participants' age")
```
## Material
The test used is Big Five Plus Personality Inventory [@BigFive-plus], being developed and validated on Romanian population (**NEEDS CITATION**) and allows the assessment of five meta-factors of personality (**Extraversion, Agreeableness, Neuroticism, Conscientiousness** and **Openness to experience**), but also 30 facets subordinated to them.

The inventory contains a number of 240 dichotomous items, 48 for the assessment of each of the five dimensions (meta-factors) and eight for each of the 30 facets. The examinee is instructed to choose between two assertions the one that best describes him/her. (e.g. **When I am at a party:** *(a) I am in the middle of the action, surrounded by others; (b) I prefer to stand aside and observe.*). 

The two answer options represents extremes of the target psychological dimension and are indented to be similar in terms of social desirability. The average time to complete the questionnaire is 35 minutes.

A research conducted by the authors of the inventory on a number of **1340 Romanian people** [@BigFive-plus] led to acceptable internal consistencies, both on the entire national normative sample and by the gender (see Table \@ref(tab:authorCronbach1) & \@ref(tab:authorCronbach2)) 

```{r authorCronbach, echo=FALSE}
  # Building Table
  cron.tab.auth <- data.frame('EXTRAVERSION', .920, .914, .917)
  colnames(cron.tab.auth) <- c("Dimension/Facet", "Male", "Female", "Normative sample")
  cron.tab.auth <- rbind(cron.tab.auth, c('- Friendliness', .742, .748, .744))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Gregariousness', .781, .767, .775))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Assertiveness', .712, .692, .702))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Activity level', .727, .669, .696))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Excitement seeking', .802, .762, .786))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cheerfulness', .716, .750, .735))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('AGREEABLENESS', .844, .826, .838))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Trust', .647, .672, .660))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Morality', .711, .703, .708))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Altruism', .655, .650, .653))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cooperation', .645, .635, .641))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Modesty', .650, .666, .660))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Sympathy', .717, .653, .705))
    
  cron.tab.auth <- rbind(cron.tab.auth, c('NEUROTICISM', .875, .877, .879))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Anxiety', .700, .700, .708))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Anger', .834, .839, .839))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Depression', .737, .717, .730))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Timidity', .623, .665, .649))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Immoderation', .779, .738, .761))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Vulnerability', .741, .742, .746))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('CONSCIENTIOUSNESS', .857, .820, .840))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Self-efficacy', .670, .675, .679))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Orderliness', .653, .647, .650))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Dutifulness', .674, .608, .648))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Achievement-striving', .655, .639, .646))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Self-discipline', .699, .596, .655))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cautiousness', .748, .704, .729))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('OPENNESS TO EXPERIENCE', .820, .809, .813))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Imagination', .653, .665, .658))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Artistic interests', .744, .702, .732))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Emotionality', .421, .510, .671))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Adventurousness', .753, .744, .750))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Intellect', .564, .579, .572))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Liberalism', .628, .587, .607))
  
  # Returning extreme values
  min.norm <- min(cron.tab.auth$`Normative sample`)
  max.norm <- max(cron.tab.auth$`Normative sample`)
  
  min.factors <- paste(cron.tab.auth[which(cron.tab.auth$`Normative sample` < .65), 1])
  min.factors <- sub("..", "", min.factors)
  min.values <- paste(cron.tab.auth[which(cron.tab.auth$`Normative sample` < .65), 4])
  min.factors <- paste(min.factors, " (", min.values, "), ", sep = "", collapse = "")
  
  kable(cron.tab.auth[1:21, ], format = "latex", digits = 2, booktabs = T, row.names = F,
        caption = "Alpha Cronbach - Authors' research on normative sample (n=1340)",
        align = c("l", "r", "r", "r"), label = "authorCronbach1")
  kable(cron.tab.auth[22:35, ], format = "latex", digits = 2, booktabs = T, row.names = F,
        caption = "Alpha Cronbach - Authors' research on normative sample (n=1340)",
        align = c("l", "r", "r", "r"), label = "authorCronbach2")
```
It can be noted that, from the authors' research, the minimum value of the Cronbach \(\alpha\) coefficient was `r min.norm`, and the maximum value was `r max.norm`, both values being obtained on the normative sample.The factors with low values of internal consistency and which pose problems regarding the reliability of the measurement are: *`r min.factors`*.

## Procedure
The analysis will involve the initial study of the internal consistency, for each scale, using the \(\alpha\) Cronbach [@Cronbach-1951] in order to calculate the internal consistency coefficient \(\alpha\) (Guttman \(\lambda\)~3~), then comparing the coefficients with the values reported by authors [@BigFive-plus].

We will then test the model in which the latent trait loads the 8 indicators, for each of the 6 facets of a dimension, and the existence of the common dimension for all 6 latent factors. After interpreting the parameters and diagnosing the models, they will be re-specified, identifying, if necessary, better explanatory models.

**In the first phase** we will present the comparative analysis of the authors regarding the internal consistency using the **alpha Cronbach method of \(\tau\)-equivalent reliability** [@Cronbach-1951], including both global indicators and those broken down by *gender* and *method of data gathering (pencil-paper or online)*. The analysis eas performed using the **psych** package [@R-psych], starting from the condition of the cumulative items, the total score resulting from summing the score of the 8 items (8 point of theoretical range), with identifying the items' negative variance and automatically recording. A non-parametric re-sampling was also used, simulating 100 samples in order to verify the stability of the parameters.

**In the second phase**, the Big Five Plus Inventory analysis will be performed according to a classical model of confirmatory factor analysis with uncorrelated second order factors, which will be analyzed using the **lavaan** package.[@R-lavaan]. Since the indicators are dichotomous, we will use the *method of estimating the thresholds of the response categories* in which each indicator becomes loaded in the latent trait and determines an active response (1-Yes) if it exceeds its threshold value, established by the item's position on the latent continuum. As an estimator, we will compute one from the categories of methods based on the least squares, namely **WLSM"**, which uses only the diagonal of the weighted matrix "W" (**DWLS**) and, for statistical tests, adjusted means. The "Satorra Bentler" version of the \(\chi\)^2^ test was used to test the overall fit, adjusting the means. [@Skrondal-2005].

## Data analysis
All analyzes were performed using: `r cite_r("r-references.bib")`

# Results
## Scales' reliability
```{r reliability, echo=FALSE, include=FALSE}
  source("02 - Consistente.R")
```
### Extraversion
```{r extraversion, echo=FALSE}
  # Generating table
  con.df <- as.data.frame(EXTRAVER$total)
  con.df <- rbind(con.df, EXT.Frien$total, EXT.Grega$total, EXT.Asser$total, 
                  EXT.Activ$total, EXT.Excit$total, EXT.Cheer$total)
  con.df <- select(con.df, c(-5, -9))
  con.df <- cbind(con.df, as.numeric(cron.tab.auth[1:7, 4]))  # Authors' Alpha
  con.df <- round(con.df, 2)
  # Adding Confidence Intervals
  ci <- c(paste(round(CI.EXTRAVER$lower.ci, 3), "-", round(CI.EXTRAVER$upper.ci, 3)),
          paste(round(CI.EXT.Frien$lower.ci, 3), "-", round(CI.EXT.Frien$upper.ci, 3)),
          paste(round(CI.EXT.Grega$lower.ci, 3), "-", round(CI.EXT.Grega$upper.ci, 3)),
          paste(round(CI.EXT.Asser$lower.ci, 3), "-", round(CI.EXT.Asser$upper.ci, 3)),
          paste(round(CI.EXT.Activ$lower.ci, 3), "-", round(CI.EXT.Activ$upper.ci, 3)),
          paste(round(CI.EXT.Excit$lower.ci, 3), "-", round(CI.EXT.Excit$upper.ci, 3)),
          paste(round(CI.EXT.Cheer$lower.ci, 3), "-", round(CI.EXT.Cheer$upper.ci, 3))
          )
  con.df <- cbind(con.df[, 1], ci, con.df[, 2:8])
  # Setting up variables' name
  Var.names <- c( "EXTRAVERSION", 
                  "Friendliness", "Gregariousness", "Assertiveness",
                  "Activity", "Excitement", "Cheerfulness")
  con.df <- cbind(Var.names, con.df)    # Name of the variables
  # Changing the names of the columns
  names(con.df) <- c("Variable", "Alpha", "CI 95%", "Std", "G6", "Avg r", "Avg SE", 
                     "Mean", "SD", "Initial")
  
  kable(con.df, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Extraversion - Global alpha Cronbach",
        align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r"))
```
```{r extraversion-boot, echo=FALSE}
  # Adding value after resampling
  alpha.boot <- c(paste(round(min(EXTRAVER$boot[, 1]), 3), "-", round(max(EXTRAVER$boot[, 1]), 3)),
                  paste(round(min(EXT.Frien$boot[, 1]), 3), "-", round(max(EXT.Frien$boot[, 1]), 3)),
                  paste(round(min(EXT.Grega$boot[, 1]), 3), "-", round(max(EXT.Grega$boot[, 1]), 3)),
                  paste(round(min(EXT.Asser$boot[, 1]), 3), "-", round(max(EXT.Asser$boot[, 1]), 3)),
                  paste(round(min(EXT.Activ$boot[, 1]), 3), "-", round(max(EXT.Activ$boot[, 1]), 3)),
                  paste(round(min(EXT.Excit$boot[, 1]), 3), "-", round(max(EXT.Excit$boot[, 1]), 3)),
                  paste(round(min(EXT.Cheer$boot[, 1]), 3), "-", round(max(EXT.Cheer$boot[, 1]), 3))
                  )
  unidim.boot <- c(paste(round(min(EXTRAVER$boot[, 7]), 3), "-", round(max(EXTRAVER$boot[, 7]), 3)),
                   paste(round(min(EXT.Frien$boot[, 7]), 3), "-", round(max(EXT.Frien$boot[, 7]), 3)),
                   paste(round(min(EXT.Grega$boot[, 7]), 3), "-", round(max(EXT.Grega$boot[, 7]), 3)),
                   paste(round(min(EXT.Asser$boot[, 7]), 3), "-", round(max(EXT.Asser$boot[, 7]), 3)),
                   paste(round(min(EXT.Activ$boot[, 7]), 3), "-", round(max(EXT.Activ$boot[, 7]), 3)),
                   paste(round(min(EXT.Excit$boot[, 7]), 3), "-", round(max(EXT.Excit$boot[, 7]), 3)),
                   paste(round(min(EXT.Cheer$boot[, 7]), 3), "-", round(max(EXT.Cheer$boot[, 7]), 3))
                   )
  gfi.boot <- c(paste(round(min(EXTRAVER$boot[, 8]), 3), "-", round(max(EXTRAVER$boot[, 8]), 3)),
                paste(round(min(EXT.Frien$boot[, 8]), 3), "-", round(max(EXT.Frien$boot[, 8]), 3)),
                paste(round(min(EXT.Grega$boot[, 8]), 3), "-", round(max(EXT.Grega$boot[, 8]), 3)),
                paste(round(min(EXT.Asser$boot[, 8]), 3), "-", round(max(EXT.Asser$boot[, 8]), 3)),
                paste(round(min(EXT.Activ$boot[, 8]), 3), "-", round(max(EXT.Activ$boot[, 8]), 3)),
                paste(round(min(EXT.Excit$boot[, 8]), 3), "-", round(max(EXT.Excit$boot[, 8]), 3)),
                paste(round(min(EXT.Cheer$boot[, 8]), 3), "-", round(max(EXT.Cheer$boot[, 8]), 3))
                )
  con.boot <- cbind.data.frame(con.df[, 2], alpha.boot, unidim.boot, gfi.boot)
  con.boot <- cbind(Var.names, con.boot)    # Name of the variables
   # Changing the names of the columns
  names(con.boot) <- c("Variable", "Base alpha", "Alpha boot", "Unidim", "GFI")
  
  kable(con.boot, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Extraversion - Global alpha Cronbach after bootstrapping",
        align = c("l", "r", "r", "r"))
```
```{r extraversion-items, echo=FALSE}
  # Generating table
  con.items <- rbind.data.frame(round(EXT.Frien$alpha.drop, 3),
                                round(EXT.Grega$alpha.drop, 3),
                                round(EXT.Asser$alpha.drop, 3),
                                round(EXT.Activ$alpha.drop, 3),
                                round(EXT.Excit$alpha.drop, 3),
                                round(EXT.Cheer$alpha.drop, 3)
                                )
  con.items <- select(con.items, c(-5, -7, -8))
  fac.alpha <- c(rep(round(EXT.Frien$total[1, 1], 3), 8),
                 rep(round(EXT.Grega$total[1, 1], 3), 8),
                 rep(round(EXT.Asser$total[1, 1], 3), 8),
                 rep(round(EXT.Activ$total[1, 1], 3), 8),
                 rep(round(EXT.Excit$total[1, 1], 3), 8),
                 rep(round(EXT.Cheer$total[1, 1], 3), 8)
                 )
  fac.names <-c(rep("Friendliness", 8),
                rep("Gregariousness", 8),
                rep("Assertiveness", 8),
                rep("Activity", 8),
                rep("Excitement", 8),
                rep("Cheerfulness", 8)
                )
  con.items <- cbind(fac.names, fac.alpha, con.items)
   # Changing the names of the columns
  names(con.items) <- c("Facet name", "Facet" ,"Deleted", "Std", "G6", "Avg r", "SE")
  
  kable(con.items[1:24,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha if item is deleted (Friendliness, Gregariousness, Assertiveness)",label = "EXT-items-1")
  kable(con.items[25:48,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha Cronbach if item is deleted (Activity level, Excitement seeking,
        Cheerfulness)", label = "EXT-items-2")
```
The results obtained for the **Extraversion dimension** and the associated facets (\(\alpha\) between `r min(con.df[2])` and `r max(con.df[2])` in our sample (n=`r n`)) do not differ much from those of the authors (\(\alpha\) between `r min(con.df[10])` and `r max(con.df[10])`), resulting in good consistency coefficients, with small estimation errors (see Table \@ref(tab:extraversion)).

After re-sampling using a number of 100 simulated samples, the values of the consistency coefficients proved to be stable both at the general construct (**Extraversion:** Base \(\alpha\)=`r con.boot[1, 2]`, Boot \(\alpha\)=`r con.boot[1, 3]`, Uniqueness=`r con.boot[1, 3]`, GFI=`r con.boot[1, 5]`) and at the level of the facets (see Table \@ref(tab:extraversion-boot)).

Analyzing the items, we found that their removal does not cause a significant increase in the internal consistency of any facet (see Tables \@ref(tab:EXT-items-1) & \@ref(tab:EXT-items-2)), therefore, both the **extraversion dimension** and its 6 facets have a good reliability and good indicators of uniqueness.

### Agreeableness
```{r agreeableness, echo=FALSE}
  # Generating table
  con.df <- as.data.frame(AGREEABL$total)
  con.df <- rbind(con.df, AGR.Altru$total, AGR.Coope$total, AGR.Modes$total, 
                  AGR.Moral$total, AGR.Sympa$total, AGR.Trust$total)
  con.df <- select(con.df, c(-5, -9))
  con.df <- cbind(con.df, as.numeric(cron.tab.auth[1:7, 4]))  # Authors' Alpha
  con.df <- round(con.df, 2)
  # Adding Confidence Intervals
  ci <- c(paste(round(CI.AGREEABL$lower.ci, 3), "-", round(CI.AGREEABL$upper.ci, 3)),
          paste(round(CI.AGR.Altru$lower.ci, 3), "-", round(CI.AGR.Altru$upper.ci, 3)),
          paste(round(CI.AGR.Coope$lower.ci, 3), "-", round(CI.AGR.Coope$upper.ci, 3)),
          paste(round(CI.AGR.Modes$lower.ci, 3), "-", round(CI.AGR.Modes$upper.ci, 3)),
          paste(round(CI.AGR.Moral$lower.ci, 3), "-", round(CI.AGR.Moral$upper.ci, 3)),
          paste(round(CI.AGR.Sympa$lower.ci, 3), "-", round(CI.AGR.Sympa$upper.ci, 3)),
          paste(round(CI.AGR.Trust$lower.ci, 3), "-", round(CI.AGR.Trust$upper.ci, 3))
          )
  con.df <- cbind(con.df[, 1], ci, con.df[, 2:8])
  # Setting up variables' name
  Var.names <- c( "AGREEABLENESS", 
                  "Altruism", "Cooperation", "Modesty",
                  "Morality", "Sympathy", "Trust")
  con.df <- cbind(Var.names, con.df)    # Name of the variables
  # Changing the names of the columns
  names(con.df) <- c("Variable", "Alpha", "CI 95%", "Std", "G6", "Avg r", "Avg SE", 
                     "Mean", "SD", "Initial")
  
  kable(con.df, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Agreeableness - Global alpha Cronbach",
        align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r"))
```
```{r agreeableness-boot, echo=FALSE}
  # Adding value after resampling
  alpha.boot <- c(paste(round(min(AGREEABL$boot[, 1]), 3), "-", round(max(AGREEABL$boot[, 1]), 3)),
                  paste(round(min(AGR.Altru$boot[, 1]), 3), "-", round(max(AGR.Altru$boot[, 1]), 3)),
                  paste(round(min(AGR.Coope$boot[, 1]), 3), "-", round(max(AGR.Coope$boot[, 1]), 3)),
                  paste(round(min(AGR.Modes$boot[, 1]), 3), "-", round(max(AGR.Modes$boot[, 1]), 3)),
                  paste(round(min(AGR.Moral$boot[, 1]), 3), "-", round(max(AGR.Moral$boot[, 1]), 3)),
                  paste(round(min(AGR.Sympa$boot[, 1]), 3), "-", round(max(AGR.Sympa$boot[, 1]), 3)),
                  paste(round(min(AGR.Trust$boot[, 1]), 3), "-", round(max(AGR.Trust$boot[, 1]), 3))
                  )
  unidim.boot <- c(paste(round(min(AGREEABL$boot[, 7]), 3), "-", round(max(AGREEABL$boot[, 7]), 3)),
                   paste(round(min(AGR.Altru$boot[, 7]), 3), "-", round(max(AGR.Altru$boot[, 7]), 3)),
                   paste(round(min(AGR.Coope$boot[, 7]), 3), "-", round(max(AGR.Coope$boot[, 7]), 3)),
                   paste(round(min(AGR.Modes$boot[, 7]), 3), "-", round(max(AGR.Modes$boot[, 7]), 3)),
                   paste(round(min(AGR.Moral$boot[, 7]), 3), "-", round(max(AGR.Moral$boot[, 7]), 3)),
                   paste(round(min(AGR.Sympa$boot[, 7]), 3), "-", round(max(AGR.Sympa$boot[, 7]), 3)),
                   paste(round(min(AGR.Trust$boot[, 7]), 3), "-", round(max(AGR.Trust$boot[, 7]), 3))
                   )
  gfi.boot <- c(paste(round(min(AGREEABL$boot[, 8]), 3), "-", round(max(AGREEABL$boot[, 8]), 3)),
                paste(round(min(AGR.Altru$boot[, 8]), 3), "-", round(max(AGR.Altru$boot[, 8]), 3)),
                paste(round(min(AGR.Coope$boot[, 8]), 3), "-", round(max(AGR.Coope$boot[, 8]), 3)),
                paste(round(min(AGR.Modes$boot[, 8]), 3), "-", round(max(AGR.Modes$boot[, 8]), 3)),
                paste(round(min(AGR.Moral$boot[, 8]), 3), "-", round(max(AGR.Moral$boot[, 8]), 3)),
                paste(round(min(AGR.Sympa$boot[, 8]), 3), "-", round(max(AGR.Sympa$boot[, 8]), 3)),
                paste(round(min(AGR.Trust$boot[, 8]), 3), "-", round(max(AGR.Trust$boot[, 8]), 3))
                )
  con.boot <- cbind.data.frame(con.df[, 2], alpha.boot, unidim.boot, gfi.boot)
  con.boot <- cbind(Var.names, con.boot)    # Name of the variables
   # Changing the names of the columns
  names(con.boot) <- c("Variable", "Base alpha", "Alpha boot", "Unidim", "GFI")
  
  kable(con.boot, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Agreeableness - Global alpha Cronbach after bootstrapping",
        align = c("l", "r", "r", "r"))
```
```{r agreeableness-items, echo=FALSE}
  # Generating table
  con.items <- rbind.data.frame(round(AGR.Altru$alpha.drop, 3),
                                round(AGR.Coope$alpha.drop, 3),
                                round(AGR.Modes$alpha.drop, 3),
                                round(AGR.Moral$alpha.drop, 3),
                                round(AGR.Sympa$alpha.drop, 3),
                                round(AGR.Trust$alpha.drop, 3)
                                )
  con.items <- select(con.items, c(-5, -7, -8))
  fac.alpha <- c(rep(round(AGR.Altru$total[1, 1], 3), 8),
                 rep(round(AGR.Coope$total[1, 1], 3), 8),
                 rep(round(AGR.Modes$total[1, 1], 3), 8),
                 rep(round(AGR.Moral$total[1, 1], 3), 8),
                 rep(round(AGR.Sympa$total[1, 1], 3), 8),
                 rep(round(AGR.Trust$total[1, 1], 3), 8)
                 )
  fac.names <-c(rep("Altruism", 8),
                rep("Cooperation", 8),
                rep("Modesty", 8),
                rep("Morality", 8),
                rep("Sympathy", 8),
                rep("Trust", 8)
                )
  con.items <- cbind(fac.names, fac.alpha, con.items)
   # Changing the names of the columns
  names(con.items) <- c("Facet name", "Facet" ,"Deleted", "Std", "G6", "Avg r", "SE")
  
  kable(con.items[1:24,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha if item is deleted (Altruism, Cooperation, Modesty)",label = "AGR-items-1")
  kable(con.items[25:48,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha Cronbach if item is deleted (Morality, Sympathy,
        Trust)", label = "AGR-items-2")
```
The results obtained for the **Agreeableness dimension** and the associated facets (\(\alpha\) between `r min(con.df[2])` and `r max(con.df[2])` in our sample (n=`r n`)) differ from those reported by the authors (\(\alpha\) between `r min(con.df[10])` and `r max(con.df[10])`)  (see Table \@ref(tab:agreeableness) for full results). The most problematic facets are Altruism (\(\alpha\) = `r con.df[2,2]`) and Cooperation (\(\alpha\) = `r con.df[3,2]`). Moreover, the Modesty and Morality facets also have internal cosistency coefficients below the conventional threshold - 0.70 (\(\alpha\) = `r con.df[5,2]`). Eliminating items from these two scales would not result in an increase of the internal consistency (see Table \@ref(tab:AGR-items-1) & \@ref(tab:AGR-items-2)).

After re-sampling using a number of 100 simulated samples, the values of the consistency coefficients proved to be stable both at the general construct (**Agreeableness:** Base \(\alpha\)=`r con.boot[1, 2]`, Boot \(\alpha\)=`r con.boot[1, 3]`, Uniqueness=`r con.boot[1, 3]`, GFI=`r con.boot[1, 5]`) and at the level of the facets (see Table \@ref(tab:agreeableness-boot)).

### Neuroticism
```{r neuroticism, echo=FALSE}
  # Generating table
  con.df <- as.data.frame(NEUROTIC$total)
  con.df <- rbind(con.df, NEU.Anxie$total, NEU.Anger$total, NEU.Depre$total, 
                  NEU.Immod$total, NEU.Timid$total, NEU.Vulne$total)
  con.df <- select(con.df, c(-5, -9))
  con.df <- cbind(con.df, as.numeric(cron.tab.auth[1:7, 4]))  # Authors' Alpha
  con.df <- round(con.df, 2)
  # Adding Confidence Intervals
  ci <- c(paste(round(CI.NEUROTIC$lower.ci, 3), "-", round(CI.NEUROTIC$upper.ci, 3)),
          paste(round(CI.NEU.Anxie$lower.ci, 3), "-", round(CI.NEU.Anxie$upper.ci, 3)),
          paste(round(CI.NEU.Anger$lower.ci, 3), "-", round(CI.NEU.Anger$upper.ci, 3)),
          paste(round(CI.NEU.Depre$lower.ci, 3), "-", round(CI.NEU.Depre$upper.ci, 3)),
          paste(round(CI.NEU.Immod$lower.ci, 3), "-", round(CI.NEU.Immod$upper.ci, 3)),
          paste(round(CI.NEU.Timid$lower.ci, 3), "-", round(CI.NEU.Timid$upper.ci, 3)),
          paste(round(CI.NEU.Vulne$lower.ci, 3), "-", round(CI.NEU.Vulne$upper.ci, 3))
          )
  con.df <- cbind(con.df[, 1], ci, con.df[, 2:8])
  # Setting up variables' name
  Var.names <- c( "NEUROTICISM", 
                  "Anxiety", "Anger", "Depression",
                  "Immoderation", "Timidity", "Vulnerability")
  con.df <- cbind(Var.names, con.df)    # Name of the variables
  # Changing the names of the columns
  names(con.df) <- c("Variable", "Alpha", "CI 95%", "Std", "G6", "Avg r", "Avg SE", 
                     "Mean", "SD", "Initial")
  
  kable(con.df, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Neuroticism - Global alpha Cronbach",
        align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r"))
```
```{r neuroticism-boot, echo=FALSE}
  # Adding value after resampling
  alpha.boot <- c(paste(round(min(NEUROTIC$boot[, 1]), 3), "-", round(max(NEUROTIC$boot[, 1]), 3)),
                  paste(round(min(NEU.Anxie$boot[, 1]), 3), "-", round(max(NEU.Anxie$boot[, 1]), 3)),
                  paste(round(min(NEU.Anger$boot[, 1]), 3), "-", round(max(NEU.Anger$boot[, 1]), 3)),
                  paste(round(min(NEU.Depre$boot[, 1]), 3), "-", round(max(NEU.Depre$boot[, 1]), 3)),
                  paste(round(min(NEU.Immod$boot[, 1]), 3), "-", round(max(NEU.Immod$boot[, 1]), 3)),
                  paste(round(min(NEU.Timid$boot[, 1]), 3), "-", round(max(NEU.Timid$boot[, 1]), 3)),
                  paste(round(min(NEU.Vulne$boot[, 1]), 3), "-", round(max(NEU.Vulne$boot[, 1]), 3))
                  )
  unidim.boot <- c(paste(round(min(NEUROTIC$boot[, 7]), 3), "-", round(max(NEUROTIC$boot[, 7]), 3)),
                   paste(round(min(NEU.Anxie$boot[, 7]), 3), "-", round(max(NEU.Anxie$boot[, 7]), 3)),
                   paste(round(min(NEU.Anger$boot[, 7]), 3), "-", round(max(NEU.Anger$boot[, 7]), 3)),
                   paste(round(min(NEU.Depre$boot[, 7]), 3), "-", round(max(NEU.Depre$boot[, 7]), 3)),
                   paste(round(min(NEU.Immod$boot[, 7]), 3), "-", round(max(NEU.Immod$boot[, 7]), 3)),
                   paste(round(min(NEU.Timid$boot[, 7]), 3), "-", round(max(NEU.Timid$boot[, 7]), 3)),
                   paste(round(min(NEU.Vulne$boot[, 7]), 3), "-", round(max(NEU.Vulne$boot[, 7]), 3))
                   )
  gfi.boot <- c(paste(round(min(NEUROTIC$boot[, 8]), 3), "-", round(max(NEUROTIC$boot[, 8]), 3)),
                paste(round(min(NEU.Anxie$boot[, 8]), 3), "-", round(max(NEU.Anxie$boot[, 8]), 3)),
                paste(round(min(NEU.Anger$boot[, 8]), 3), "-", round(max(NEU.Anger$boot[, 8]), 3)),
                paste(round(min(NEU.Depre$boot[, 8]), 3), "-", round(max(NEU.Depre$boot[, 8]), 3)),
                paste(round(min(NEU.Immod$boot[, 8]), 3), "-", round(max(NEU.Immod$boot[, 8]), 3)),
                paste(round(min(NEU.Timid$boot[, 8]), 3), "-", round(max(NEU.Timid$boot[, 8]), 3)),
                paste(round(min(NEU.Vulne$boot[, 8]), 3), "-", round(max(NEU.Vulne$boot[, 8]), 3))
                )
  con.boot <- cbind.data.frame(con.df[, 2], alpha.boot, unidim.boot, gfi.boot)
  con.boot <- cbind(Var.names, con.boot)    # Name of the variables
   # Changing the names of the columns
  names(con.boot) <- c("Variable", "Base alpha", "Alpha boot", "Unidim", "GFI")
  
  kable(con.boot, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Neuroticism - Global alpha Cronbach after bootstrapping",
        align = c("l", "r", "r", "r"))
```
```{r neuroticism-items, echo=FALSE}
  # Generating table
  con.items <- rbind.data.frame(round(NEU.Anxie$alpha.drop, 3),
                                round(NEU.Anger$alpha.drop, 3),
                                round(NEU.Depre$alpha.drop, 3),
                                round(NEU.Immod$alpha.drop, 3),
                                round(NEU.Timid$alpha.drop, 3),
                                round(NEU.Vulne$alpha.drop, 3)
                                )
  con.items <- select(con.items, c(-5, -7, -8))
  fac.alpha <- c(rep(round(NEU.Anxie$total[1, 1], 3), 8),
                 rep(round(NEU.Anger$total[1, 1], 3), 8),
                 rep(round(NEU.Depre$total[1, 1], 3), 8),
                 rep(round(NEU.Immod$total[1, 1], 3), 8),
                 rep(round(NEU.Timid$total[1, 1], 3), 8),
                 rep(round(NEU.Vulne$total[1, 1], 3), 8)
                 )
  fac.names <-c(rep("Anxiety", 8),
                rep("Anger", 8),
                rep("Depression", 8),
                rep("Immoderation", 8),
                rep("Timidity", 8),
                rep("Vulnerability", 8)
                )
  con.items <- cbind(fac.names, fac.alpha, con.items)
   # Changing the names of the columns
  names(con.items) <- c("Facet name", "Facet" ,"Deleted", "Std", "G6", "Avg r", "SE")
  
  kable(con.items[1:24,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha if item is deleted (Anxiety, Anger, Depression)",label = "NEU-items-1")
  kable(con.items[25:48,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha Cronbach if item is deleted (Immoderation, Timidity,
        Vulnerability)", label = "NEU-items-2")
```
The results obtained for the **Neuroticism dimension** and its subordinated facets (\(\alpha\) between `r min(con.df[2])` and `r max(con.df[2])` in our sample (n=`r n`)) are similar to  those of the authors (\(\alpha\) between `r min(con.df[10])` and `r max(con.df[10])`). Adequate consistency coefficients, with small estimation errors, were found for the facet levels. A high alpha coeffiecient was obtained at the domain level (\(\alpha\) = `r con.df[1,10]`), suggesting that some items may be redundant (see Table \@ref(tab:neuroticism)).

After bootstrapping, internal consistency coefficients proved to be stable both at the general construct (**Neuroticism:** Base \(\alpha\)=`r con.boot[1, 2]`, Boot \(\alpha\)=`r con.boot[1, 3]`, Uniqueness=`r con.boot[1, 3]`, GFI=`r con.boot[1, 5]`) and at the level of the facets (see Table \@ref(tab:neuroticism-boot)).

Similarly to the analyses for Extraversion and Agreeableness, we found that removing items would not cause a significant increase in the internal consistency of any facet (see Tables \@ref(tab:NEU-items-1) & \@ref(tab:NEU-items-2)). We conclude that both the **neuroticism dimension** and its 6 facets have a good reliability and good indicators of uniqueness.

### Conscientiousness
```{r conscientiousness, echo=FALSE}
  # Generating table
  con.df <- as.data.frame(CONSCIEN$total)
  con.df <- rbind(con.df, CON.SelfE$total, CON.Order$total, CON.Dutif$total, 
                  CON.Achie$total, CON.SelfD$total, CON.Cauti$total)
  con.df <- select(con.df, c(-5, -9))
  con.df <- cbind(con.df, as.numeric(cron.tab.auth[1:7, 4]))  # Authors' Alpha
  con.df <- round(con.df, 2)
  # Adding Confidence Intervals
  ci <- c(paste(round(CI.CONSCIEN$lower.ci, 3), "-", round(CI.CONSCIEN$upper.ci, 3)),
          paste(round(CI.CON.SelfE$lower.ci, 3), "-", round(CI.CON.SelfE$upper.ci, 3)),
          paste(round(CI.CON.Order$lower.ci, 3), "-", round(CI.CON.Order$upper.ci, 3)),
          paste(round(CI.CON.Dutif$lower.ci, 3), "-", round(CI.CON.Dutif$upper.ci, 3)),
          paste(round(CI.CON.Achie$lower.ci, 3), "-", round(CI.CON.Achie$upper.ci, 3)),
          paste(round(CI.CON.SelfD$lower.ci, 3), "-", round(CI.CON.SelfD$upper.ci, 3)),
          paste(round(CI.CON.Cauti$lower.ci, 3), "-", round(CI.CON.Cauti$upper.ci, 3))
          )
  con.df <- cbind(con.df[, 1], ci, con.df[, 2:8])
  # Setting up variables' name
  Var.names <- c( "CONSCIENTIOUSNESS", 
                  "Self Efficacy", "Order", "Dutifulness",
                  "Achievement striving", "Self Discipline", "Cautiousness")
  con.df <- cbind(Var.names, con.df)    # Name of the variables
  # Changing the names of the columns
  names(con.df) <- c("Variable", "Alpha", "CI 95%", "Std", "G6", "Avg r", "Avg SE", 
                     "Mean", "SD", "Initial")
  
  kable(con.df, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Conscientiousness - Global alpha Cronbach",
        align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r"))
```
```{r conscientiousness-boot, echo=FALSE}
  # Adding value after resampling
  alpha.boot <- c(paste(round(min(CONSCIEN$boot[, 1]), 3), "-", round(max(CONSCIEN$boot[, 1]), 3)),
                  paste(round(min(CON.SelfE$boot[, 1]), 3), "-", round(max(CON.SelfE$boot[, 1]), 3)),
                  paste(round(min(CON.Order$boot[, 1]), 3), "-", round(max(CON.Order$boot[, 1]), 3)),
                  paste(round(min(CON.Dutif$boot[, 1]), 3), "-", round(max(CON.Dutif$boot[, 1]), 3)),
                  paste(round(min(CON.Achie$boot[, 1]), 3), "-", round(max(CON.Achie$boot[, 1]), 3)),
                  paste(round(min(CON.SelfD$boot[, 1]), 3), "-", round(max(CON.SelfD$boot[, 1]), 3)),
                  paste(round(min(CON.Cauti$boot[, 1]), 3), "-", round(max(CON.Cauti$boot[, 1]), 3))
                  )
  unidim.boot <- c(paste(round(min(CONSCIEN$boot[, 7]), 3), "-", round(max(CONSCIEN$boot[, 7]), 3)),
                   paste(round(min(CON.SelfE$boot[, 7]), 3), "-", round(max(CON.SelfE$boot[, 7]), 3)),
                   paste(round(min(CON.Order$boot[, 7]), 3), "-", round(max(CON.Order$boot[, 7]), 3)),
                   paste(round(min(CON.Dutif$boot[, 7]), 3), "-", round(max(CON.Dutif$boot[, 7]), 3)),
                   paste(round(min(CON.Achie$boot[, 7]), 3), "-", round(max(CON.Achie$boot[, 7]), 3)),
                   paste(round(min(CON.SelfD$boot[, 7]), 3), "-", round(max(CON.SelfD$boot[, 7]), 3)),
                   paste(round(min(CON.Cauti$boot[, 7]), 3), "-", round(max(CON.Cauti$boot[, 7]), 3))
                   )
  gfi.boot <- c(paste(round(min(CONSCIEN$boot[, 8]), 3), "-", round(max(CONSCIEN$boot[, 8]), 3)),
                paste(round(min(CON.SelfE$boot[, 8]), 3), "-", round(max(CON.SelfE$boot[, 8]), 3)),
                paste(round(min(CON.Order$boot[, 8]), 3), "-", round(max(CON.Order$boot[, 8]), 3)),
                paste(round(min(CON.Dutif$boot[, 8]), 3), "-", round(max(CON.Dutif$boot[, 8]), 3)),
                paste(round(min(CON.Achie$boot[, 8]), 3), "-", round(max(CON.Achie$boot[, 8]), 3)),
                paste(round(min(CON.SelfD$boot[, 8]), 3), "-", round(max(CON.SelfD$boot[, 8]), 3)),
                paste(round(min(CON.Cauti$boot[, 8]), 3), "-", round(max(CON.Cauti$boot[, 8]), 3))
                )
  con.boot <- cbind.data.frame(con.df[, 2], alpha.boot, unidim.boot, gfi.boot)
  con.boot <- cbind(Var.names, con.boot)    # Name of the variables
   # Changing the names of the columns
  names(con.boot) <- c("Variable", "Base alpha", "Alpha boot", "Unidim", "GFI")
  
  kable(con.boot, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Conscientiousness - Global alpha Cronbach after bootstrapping",
        align = c("l", "r", "r", "r"))
```
```{r conscientiousness-items, echo=FALSE}
  # Generating table
  con.items <- rbind.data.frame(round(CON.SelfE$alpha.drop, 3),
                                round(CON.Order$alpha.drop, 3),
                                round(CON.Dutif$alpha.drop, 3),
                                round(CON.Achie$alpha.drop, 3),
                                round(CON.SelfD$alpha.drop, 3),
                                round(CON.Cauti$alpha.drop, 3)
                                )
  con.items <- select(con.items, c(-5, -7, -8))
  fac.alpha <- c(rep(round(CON.SelfE$total[1, 1], 3), 8),
                 rep(round(CON.Order$total[1, 1], 3), 8),
                 rep(round(CON.Dutif$total[1, 1], 3), 8),
                 rep(round(CON.Achie$total[1, 1], 3), 8),
                 rep(round(CON.SelfD$total[1, 1], 3), 8),
                 rep(round(CON.Cauti$total[1, 1], 3), 8)
                 )
  fac.names <-c(rep("Self Efficacy", 8),
                rep("Order", 8),
                rep("Dutifulness", 8),
                rep("Achievement striving", 8),
                rep("Self Discipline", 8),
                rep("Cautiousness", 8)
                )
  con.items <- cbind(fac.names, fac.alpha, con.items)
   # Changing the names of the columns
  names(con.items) <- c("Facet name", "Facet" ,"Deleted", "Std", "G6", "Avg r", "SE")
  
  kable(con.items[1:24,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha if item is deleted (Self Efficacy, Order, Dutifulness)",label = "CON-items-1")
  kable(con.items[25:48,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha Cronbach if item is deleted (Achievement striving, Self Discipline, Cautiousness)", label = "CON-items-2")
```
The results obtained for the **Conscientiousness dimension** and the associated facets (\(\alpha\) between `r min(con.df[2])` and `r max(con.df[2])` in our sample (n=`r n`)) are close to those of the authors (although slightly smaller) (\(\alpha\) between `r min(con.df[10])` and `r max(con.df[10])`), with the exception of Dutifulness ((\(\alpha\) = `r con.df[4,2]`). Analyzing the items, we found that their removal does not cause a significant increase in the internal consistency of any facet (see Tables \@ref(tab:CON-items-1) & \@ref(tab:CON-items-2)).

The values of the consistency coefficients proved to be stable after bootstrapping, both for the general domain (**Conscientiousness:** Base \(\alpha\)=`r con.boot[1, 2]`, Boot \(\alpha\)=`r con.boot[1, 3]`, Uniqueness=`r con.boot[1, 3]`, GFI=`r con.boot[1, 5]`) and for the facets (see Table \@ref(tab:conscientiousness-boot)).

### Openness
```{r openness, echo=FALSE}
  # Generating table
  con.df <- as.data.frame(OPENNESS$total)
  con.df <- rbind(con.df, OPE.Imagi$total, OPE.Artis$total, OPE.Emoti$total, 
                  OPE.Adven$total, OPE.Intel$total, OPE.Liber$total)
  con.df <- select(con.df, c(-5, -9))
  con.df <- cbind(con.df, as.numeric(cron.tab.auth[1:7, 4]))  # Authors' Alpha
  con.df <- round(con.df, 2)
  # Adding Confidence Intervals
  ci <- c(paste(round(CI.OPENNESS$lower.ci, 3), "-", round(CI.OPENNESS$upper.ci, 3)),
          paste(round(CI.OPE.Imagi$lower.ci, 3), "-", round(CI.OPE.Imagi$upper.ci, 3)),
          paste(round(CI.OPE.Artis$lower.ci, 3), "-", round(CI.OPE.Artis$upper.ci, 3)),
          paste(round(CI.OPE.Emoti$lower.ci, 3), "-", round(CI.OPE.Emoti$upper.ci, 3)),
          paste(round(CI.OPE.Adven$lower.ci, 3), "-", round(CI.OPE.Adven$upper.ci, 3)),
          paste(round(CI.OPE.Intel$lower.ci, 3), "-", round(CI.OPE.Intel$upper.ci, 3)),
          paste(round(CI.OPE.Liber$lower.ci, 3), "-", round(CI.OPE.Liber$upper.ci, 3))
          )
  con.df <- cbind(con.df[, 1], ci, con.df[, 2:8])
  # Setting up variables' name
  Var.names <- c( "OPENESS", 
                  "Imagination", "Artistic intrest", "Emotionality",
                  "Adventure spirit", "Intellect", "Liberalism")
  con.df <- cbind(Var.names, con.df)    # Name of the variables
  # Changing the names of the columns
  names(con.df) <- c("Variable", "Alpha", "CI 95%", "Std", "G6", "Avg r", "Avg SE", 
                     "Mean", "SD", "Initial")
  
  kable(con.df, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Openess - Global alpha Cronbach",
        align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r"))
```
```{r openness-boot, echo=FALSE}
  # Adding value after resampling
  alpha.boot <- c(paste(round(min(OPENNESS$boot[, 1]), 3), "-", round(max(OPENNESS$boot[, 1]), 3)),
                  paste(round(min(OPE.Imagi$boot[, 1]), 3), "-", round(max(OPE.Imagi$boot[, 1]), 3)),
                  paste(round(min(OPE.Artis$boot[, 1]), 3), "-", round(max(OPE.Artis$boot[, 1]), 3)),
                  paste(round(min(OPE.Emoti$boot[, 1]), 3), "-", round(max(OPE.Emoti$boot[, 1]), 3)),
                  paste(round(min(OPE.Adven$boot[, 1]), 3), "-", round(max(OPE.Adven$boot[, 1]), 3)),
                  paste(round(min(OPE.Intel$boot[, 1]), 3), "-", round(max(OPE.Intel$boot[, 1]), 3)),
                  paste(round(min(OPE.Liber$boot[, 1]), 3), "-", round(max(OPE.Liber$boot[, 1]), 3))
                  )
  unidim.boot <- c(paste(round(min(OPENNESS$boot[, 7]), 3), "-", round(max(OPENNESS$boot[, 7]), 3)),
                   paste(round(min(OPE.Imagi$boot[, 7]), 3), "-", round(max(OPE.Imagi$boot[, 7]), 3)),
                   paste(round(min(OPE.Artis$boot[, 7]), 3), "-", round(max(OPE.Artis$boot[, 7]), 3)),
                   paste(round(min(OPE.Emoti$boot[, 7]), 3), "-", round(max(OPE.Emoti$boot[, 7]), 3)),
                   paste(round(min(OPE.Adven$boot[, 7]), 3), "-", round(max(OPE.Adven$boot[, 7]), 3)),
                   paste(round(min(OPE.Intel$boot[, 7]), 3), "-", round(max(OPE.Intel$boot[, 7]), 3)),
                   paste(round(min(OPE.Liber$boot[, 7]), 3), "-", round(max(OPE.Liber$boot[, 7]), 3))
                   )
  gfi.boot <- c(paste(round(min(OPENNESS$boot[, 8]), 3), "-", round(max(OPENNESS$boot[, 8]), 3)),
                paste(round(min(OPE.Imagi$boot[, 8]), 3), "-", round(max(OPE.Imagi$boot[, 8]), 3)),
                paste(round(min(OPE.Artis$boot[, 8]), 3), "-", round(max(OPE.Artis$boot[, 8]), 3)),
                paste(round(min(OPE.Emoti$boot[, 8]), 3), "-", round(max(OPE.Emoti$boot[, 8]), 3)),
                paste(round(min(OPE.Adven$boot[, 8]), 3), "-", round(max(OPE.Adven$boot[, 8]), 3)),
                paste(round(min(OPE.Intel$boot[, 8]), 3), "-", round(max(OPE.Intel$boot[, 8]), 3)),
                paste(round(min(OPE.Liber$boot[, 8]), 3), "-", round(max(OPE.Liber$boot[, 8]), 3))
                )
  con.boot <- cbind.data.frame(con.df[, 2], alpha.boot, unidim.boot, gfi.boot)
  con.boot <- cbind(Var.names, con.boot)    # Name of the variables
   # Changing the names of the columns
  names(con.boot) <- c("Variable", "Base alpha", "Alpha boot", "Unidim", "GFI")
  
  kable(con.boot, format = "latex", digits = 3, booktabs = T, row.names = F,
        caption = "Openess - Global alpha Cronbach after bootstrapping",
        align = c("l", "r", "r", "r"))
```
```{r openness-items, echo=FALSE}
  # Generating table
  con.items <- rbind.data.frame(round(OPE.Imagi$alpha.drop, 3),
                                round(OPE.Artis$alpha.drop, 3),
                                round(OPE.Emoti$alpha.drop, 3),
                                round(OPE.Adven$alpha.drop, 3),
                                round(OPE.Intel$alpha.drop, 3),
                                round(OPE.Liber$alpha.drop, 3)
                                )
  con.items <- select(con.items, c(-5, -7, -8))
  fac.alpha <- c(rep(round(OPE.Imagi$total[1, 1], 3), 8),
                 rep(round(OPE.Artis$total[1, 1], 3), 8),
                 rep(round(OPE.Emoti$total[1, 1], 3), 8),
                 rep(round(OPE.Adven$total[1, 1], 3), 8),
                 rep(round(OPE.Intel$total[1, 1], 3), 8),
                 rep(round(OPE.Liber$total[1, 1], 3), 8)
                 )
  fac.names <-c(rep("Imagination", 8),
                rep("Artistic interest", 8),
                rep("Emotionality", 8),
                rep("Adventure spirit", 8),
                rep("Intellect", 8),
                rep("Liberalism", 8)
                )
  con.items <- cbind(fac.names, fac.alpha, con.items)
   # Changing the names of the columns
  names(con.items) <- c("Facet name", "Facet" ,"Deleted", "Std", "G6", "Avg r", "SE")
  
  kable(con.items[1:24,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha if item is deleted (Imagination, Artistic interest, Emotionality)",label = "OPE-items-1")
  kable(con.items[25:48,], format = "latex", digits = 3, booktabs = T, row.names = T, align = "r",
        caption = "Alpha Cronbach if item is deleted (Adventure spirit, Intellect, Liberalism)", label = "OPE-items-2")
```
The results obtained for the **Openness dimension** and the associated facets (\(\alpha\) between `r min(con.df[2])` and `r max(con.df[2])` in our sample (n=`r n`)) are smaller when compared to  those reported by the authors of the instrument(\(\alpha\) between `r min(con.df[10])` and `r max(con.df[10])`) (see Table \@ref(tab:openness)).The most problematic facets are Intellect (\(\alpha\) = `r con.df[6,2]`) and Liberalism (\(\alpha\) = `r con.df[7,2]`).

After re-sampling using a number of 100 simulated samples, the values of the consistency coefficients proved to be stable both at the general construct (**Openness:** Base \(\alpha\)=`r con.boot[1, 2]`, Boot \(\alpha\)=`r con.boot[1, 3]`, Uniqueness=`r con.boot[1, 3]`, GFI=`r con.boot[1, 5]`) and at the level of the facets (see Table \@ref(tab:openness-boot)).

Analyzing the items, we found the removal of item 230 from the Intellect scale would result in a small increase in the internal consistency of the Intellect facet. No other items could be deleted in order to improve the internal consistency coefficients for this domain\. (see Tables \@ref(tab:OPE-items-1) & \@ref(tab:OPE-items-2)).

## Data screening and descriptive statistics
```{r screening, echo=FALSE, include=FALSE}
  source("03 - Data screening.R")
  # Extraversion results
  min.mean.EXT <- round(min(AGR.de[1:6, 2]), 2); max.mean.AGR <- round(max(AGR.de[1:6, 2]), 2)
  min.sd.EXT <- round(min(AGR.de[1:6, 3]), 2); max.sd.AGR <- round(max(AGR.de[1:6, 3]), 2)
  mean.EXT <- round(AGR.de[7, 2], 2); sd.EXT <- round(AGR.de[7, 3], 2)
  min.AD.EXT <- round(min(AGR.de[1:6, 12]), 2); max.AD.AGR <- round(max(AGR.de[1:6, 12]), 2)
  min.p.EXT <- round(min(AGR.de[1:6, 13]), 2); max.p.AGR <- round(max(AGR.de[1:6, 13]), 2)
  AD.EXT <- round(AGR.de[7, 12], 2); p.EXT <- round(AGR.de[7, 13], 2)
  min.K.EXT <- round(min(AGR.de[, 9]), 2); max.K.AGR <- round(max(AGR.de[, 9]), 2)
  min.S.EXT <- round(min(AGR.de[, 8]), 2); max.S.AGR <- round(max(AGR.de[, 8]), 2)
  se.K.EXT <- round(min(AGR.de[1, 11]), 2); se.S.AGR <- round(min(AGR.de[1, 10]), 2)
  # Agreeableness results
  min.mean.AGR <- round(min(AGR.de[1:6, 2]), 2); max.mean.EXT <- round(max(AGR.de[1:6, 2]), 2)
  min.sd.AGR <- round(min(AGR.de[1:6, 3]), 2); max.sd.EXT <- round(max(AGR.de[1:6, 3]), 2)
  mean.AGR <- round(AGR.de[7, 2], 2); sd.EXT <- round(AGR.de[7, 3], 2)
  min.AD.AGR <- round(min(AGR.de[1:6, 12]), 2); max.AD.EXT <- round(max(AGR.de[1:6, 12]), 2)
  min.p.AGR <- round(min(AGR.de[1:6, 13]), 2); max.p.EXT <- round(max(AGR.de[1:6, 13]), 2)
  AD.AGR <- round(AGR.de[7, 12], 2); p.EXT <- round(AGR.de[7, 13], 2)
  min.K.AGR <- round(min(AGR.de[, 9]), 2); max.K.EXT <- round(max(AGR.de[, 9]), 2)
  min.S.AGR <- round(min(AGR.de[, 8]), 2); max.S.EXT <- round(max(AGR.de[, 8]), 2)
  se.K.AGR <- round(min(AGR.de[1, 11]), 2); se.S.EXT <- round(min(AGR.de[1, 10]), 2)
```
### Extraversion
```{r extraversion-desc}
  kable(EXT.de, format = "latex", digits = 2, booktabs = T,
        caption = "Descriptive statistics for Extraversion") %>% 
  kable_styling(latex_options="scale_down")
```
The **"Extraversion"** dimension have facets averages between `r min.mean.EXT` (sd=`r min.sd.EXT`) and `r max.mean.EXT` (sd=`r max.sd.EXT`), while the dimension's mean are `r mean.EXT` (sd=`r sd.EXT`). Unfortunately, the assumption of univariate normality is **not fulfilled** for any facet (Anderson-Darling test between `r min.AD.EXT`, p=`r min.p.EXT` and `r max.AD.EXT`, p=`r max.p.EXT`) nor for the global dimension (Anderson-Darling test=`r AD.EXT`, p=`r p.EXT`) (see Table \@ref(tab:extraversion-desc)).

All variables are platykurtic (Kurtosis between `r min.K.EXT` and `r max.K.EXT`, SE=`r se.K.EXT `) and except **Assertiveness**, left skewed (Skewness between `r min.S.EXT` and `r max.S.EXT`, SE=`r se.S.EXT`), so an assessment of extreme values will be required, but no extreme values were identified.
### Agreeableness
```{r agreeableness-desc}
  kable(AGR.de, format = "latex", digits = 2, booktabs = T,
        caption = "Descriptive statistics for Agreeableness") %>% 
  kable_styling(latex_options="scale_down")
```
The **"Agreeableness"** dimension have facets averages between `r min.mean.AGR` (sd=`r min.sd.AGR`) and `r max.mean.AGR` (sd=`r max.sd.AGR`), while the dimension's mean are `r mean.AGR` (sd=`r sd.AGR`). Unfortunately, the assumption of univariate normality is **not fulfilled** for any facet (Anderson-Darling test between `r min.AD.AGR`, p=`r min.p.AGR` and `r max.AD.AGR`, p=`r max.p.AGR`) nor for the global dimension (Anderson-Darling test=`r AD.AGR`, p=`r p.AGR`) (see Table \@ref(tab:agreeableness-desc)).

All variables except **Morality** are platykurtic (Kurtosis between `r min.K.AGR` and `r max.K.AGR`, SE=`r se.K.AGR`) the last being leptokurtic. Regarding symmetry, all variables are left skewed (Skewness between `r min.S.AGR` and `r max.S.AGR`, SE=`r se.S.AHR`), however **Modesty** seems to be symmetric, so an assessment of extreme values will be required.



### Neuroticism

### Conscientiousness

### Openness

## Confirmatory Factor Analisys


# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
