---
title             : "Factorial structure of the indicators in Big Five Plus Inventory"
shorttitle        : "Factorial structure of the indicators in Big Five Plus Inventory"
author: 
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Ovidius University Campus, Aleea Universității, No. 2, Constanța, Romania"
    email         : "copariuc@gmail.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Data analysis
  - name          : "Gabriela Nicuță"
    affiliation   : "3"
    role:
      - Writing - Systematic review
      - Writing - Data analysis
      - Proofreading
  - name          : "Ticu Constantin"
    affiliation   : "3"
    role:
      - Data provider
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "Ovidius University, Constanta, Romania"
  - id            : "2"
    institution   : "Bucharest University, Bucharest, Romania"
  - id            : "3"
    institution   : "Al. I. Cuza University, Iassy, Romania"
authornote: |
  
  The authors thanks Prof. Dr. Constantin Ticu and the PsihoProfile team for making available over 14000 data used in this analysis.
  
  The data in this paper comes form the Romanian version of BigFive Plus inventory[@BigFive-plus], being collected online through the [PsihoProfile site](http://www.psihoprofile.ro/)
abstract: |
  TO BE DONE AT THE END
keywords          : "BigFive, Confirmatory Factor Analysis, Reliability analysis"
wordcount         : "5138 words in text body, 624 words in reference section"
bibliography      : ["r-references.bib", "Big Five Plus.bib"]
link-citations    : TRUE
biblio-style      : "apalike"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : yes
documentclass     : "apa7"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - \usepackage[document]{ragged2e}
---

```{r setup, include = FALSE}
  # Including necessary libraries
  library(papaja); library(knitr)
  # Including references file for R libraries
  r_refs("r-references.bib")
```

```{r analysis-preferences}
  # Seed for random number generation
  set.seed(4482)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
\justify
In this paper we aimed to conduct an exploratory study on the **analysis of how the theoretical Big Five model is supported by data**. The volume of the data collected, even is it is very large and gives power to the study, does not constitute a representative sample because no sampling technique was used, but represents the results of tests performed with the Big Five Plus Personality Inventory [@BigFive-plus] during 2015-2020 on the population of Romania. The answers resulted either from an online administration using the [PsihoProfile site](http://www.psihoprofile.ro/), or from the classic administration, pencil-paper, followed by the introduction of the answers in the platform in order to automatically rate and generate assessment's protocols. 

Basically, the manifest variables represent the 240 dichotomous items of the **BigFive Plus Personality Inventory**, the analysis falling into the domain of confirmatory factor analysis using categorical indicators, more precisely dichotomous, and implies a specific approach.

The model does not provide for the existence of indicators loaded in more than one latent trait, each latent factor loading 8 indicators, therefore they will also represent categorical latent variables, because an amplitude of 8 points cannot qualify them as continuous variables.

The latent factors that load the 8 indicators are, in turn, loaded by one of the five Big Five dimensions, resulting in a *second-order factor analysis model* [@Byrne-2010] with uncorrelated second-order factors, which are represented as follows:

+ **Extraversion**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Friendliness*, *Gregariousness*, *Assertiveness*, *Activity level*, *Excitement seeking* and *Cheerfulness*.

+ **Agreeableness**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Trust*, *Morality*, *Altruism*, *Cooperation*, *Modesty* and *Sympathy*.

+ **Neuroticism**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Anxiety*, *Anger*, *Depression*, *Timidity*, *Immoderation* and *Vulnerability*.

+ **Conscientiousness**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Self-efficacy*, *Orderliness*, *Dutifulness*, *Achievement-striving*, *Self-discipline* și *Cautiousness*.

+ **Openness to experience**, exogenous latent variable that loads a number of 6 endogenous latent variables: *Imagination*, *Artistic interests*, *Emotionality*, *Adventurousness*, *Intellect* and *Liberalism*.

## Participants
```{r participants, echo = F, include = F}
 # Computing data
  source("01 - Lotul de cercetare.R")
  # Returning values - n
  n <- gender$output.table[3]
  # Returning values - n by gender
  n.male <- gender$output.table[1]
  n.male.prc <- gender$output.table[4]
  n.female <- gender$output.table[2]
  n.female.prc <- gender$output.table[5]
  # Returning values - n by educational level
  n.st.lic <- studies$output.table[7]
  n.st.lic.prc <- studies$output.table[18]
  n.st.hsc <- studies$output.table[5]
  n.st.hsc.prc <- studies$output.table[16]
  n.st.mst <- studies$output.table[8]
  n.st.mst.prc <- studies$output.table[19]
  n.st.phs <- studies$output.table[6]
  n.st.phs.prc <- studies$output.table[17]
  n.st.art <- studies$output.table[4]
  n.st.art.prc <- studies$output.table[15]
  n.nost <- studies$output.table[10]
  n.nost.prc <- studies$output.table[21]
  # Returning values - n by Type of data gathering
  n.paper <- online$output.table[1]
  n.paper.prc <- online$output.table[4]
  n.online <- online$output.table[2]
  n.online.prc <- online$output.table[5]
```
A total of *`r n`* protocols were collected, administered to a number of *`r n.male` males (`r n.male.prc `%)* and *`r n.female` females (`r n.female.prc`%)* (see Table \@ref(tab:gender)), most of them being *university graduates (n=`r n.st.lic`, representing `r n.st.lic.prc`%)*, followed by *high school graduated (n=`r n.st.hsc`, representing `r n.st.hsc.prc`%)* and the persons with *master's degrees (n=`r n.st.mst`, representing `r n.st.mst.prc`%)*. The research group also contains graduates of *post-secondary schools (n=`r n.st.phs`, representing `r n.st.phs.prc`%)* and graduates of *arts and crafts schools (n=`r n.st.art`, representing `r n.st.art.prc`%)*, the other categories being much less represented. (see Table \@ref(tab:education))

```{r gender, echo=FALSE}
  kable(gender$output.table, format = "latex", digits = 2, booktabs = T,
        caption = "Participants' gender")
```
```{r education, echo=FALSE}
   kable(studies$output.table, format = "latex", digits = 2, booktabs = T,
         caption = "Participants' educational level")
```

We note, however, that a large number of people did not specify the level of education *(n=`r n.nost`, reprezentând `r n.nost.prc`%)*, which will be removed from the analysis that involves the use of this variabile (see Table \@ref(tab:education)).

Regarding the data gathering method, a number of *`r n.paper` protocols* were administered in *paper-pencil form (`r n.paper.prc`%), `r n.online` protocols* being collected directly *online (`r n.online.prc`%)* (see Table \@ref(tab:gather))

```{r gather, echo=FALSE}
   kable(online$output.table, format = "latex", digits = 2, booktabs = T,
         caption = "Type of data gathering")
```

Respondents ranged in age from *min=`r age[2]`* and *max=`r age[6]`* years, with a *median age of `r age[4]`* years *(m=`r age[2]`, sd=`r age[3]`)* (see Table \@ref(tab:age))

```{r age, echo=FALSE}
   kable(age, format = "latex", digits = 2, booktabs = T, row.names = F,
         col.names = c("n", "mean", "sd", "median", "min", "max", "range", "skewness", "kurtosis"),
         caption = "Participants' age")
```

## Material
The test used is Big Five Plus Personality Inventory [@BigFive-plus], being developed and validated on Romanian population (**NEEDS CITATION**) and allows the assessment of five meta-factors of personality (**Extraversion, Agreeableness, Neuroticism, Conscientiousness** and **Openness to experience**), but also 30 facets subordinated to them.

The inventory contains a number of 240 dichotomous items, 48 for the assessment of each of the five dimensions (meta-factors) and eight for each of the 30 facets. The examinee is instructed to choose between two assertions the one that best describes him/her. (e.g. **When I am at a party:** *(a) I am in the middle of the action, surrounded by others; (b) I prefer to stand aside and observe.*). 

The two answer options represents extremes of the target psychological dimension and are indented to be similar in terms of social desirability. The average time to complete the questionnaire is 35 minutes.

A research conducted by the authors of the inventory on a number of **1340 Romanian people** [@BigFive-plus] led to acceptable internal consistencies, both on the entire national normative sample and by the gender (see Table \@ref(tab:authorCronbach1) & \@ref(tab:authorCronbach2)) 

```{r authorCronbach, echo=FALSE}
  # Building Table
  cron.tab.auth <- data.frame('EXTRAVERSION', .920, .914, .917)
  colnames(cron.tab.auth) <- c("Dimension/Facet", "Male", "Female", "Normative sample")
  cron.tab.auth <- rbind(cron.tab.auth, c('- Friendliness', .742, .748, .744))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Gregariousness', .781, .767, .775))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Assertiveness', .712, .692, .702))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Activity level', .727, .669, .696))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Excitement seeking', .802, .762, .786))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cheerfulness', .716, .750, .735))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('AGREEABLENESS', .844, .826, .838))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Trust', .647, .672, .660))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Morality', .711, .703, .708))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Altruism', .655, .650, .653))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cooperation', .645, .635, .641))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Modesty', .650, .666, .660))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Sympathy', .717, .653, .705))
    
  cron.tab.auth <- rbind(cron.tab.auth, c('NEUROTICISM', .875, .877, .879))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Anxiety', .700, .700, .708))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Anger', .834, .839, .839))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Depression', .737, .717, .730))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Timidity', .623, .665, .649))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Immoderation', .779, .738, .761))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Vulnerability', .741, .742, .746))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('CONSCIENTIOUSNESS', .857, .820, .840))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Self-efficacy', .670, .675, .679))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Orderliness', .653, .647, .650))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Dutifulness', .674, .608, .648))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Achievement-striving', .655, .639, .646))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Self-discipline', .699, .596, .655))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Cautiousness', .748, .704, .729))
  
  cron.tab.auth <- rbind(cron.tab.auth, c('OPENNESS TO EXPERIENCE', .820, .809, .813))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Imagination', .653, .665, .658))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Artistic interests', .744, .702, .732))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Emotionality', .421, .510, .671))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Adventurousness', .753, .744, .750))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Intellect', .564, .579, .572))
  cron.tab.auth <- rbind(cron.tab.auth, c('- Liberalism', .628, .587, .607))
  
  # Returning extreme values
  min.norm <- min(cron.tab.auth$`Normative sample`)
  max.norm <- max(cron.tab.auth$`Normative sample`)
  
  min.factors <- paste(cron.tab.auth[which(cron.tab.auth$`Normative sample` < .65), 1])
  min.factors <- sub("..", "", min.factors)
  min.values <- paste(cron.tab.auth[which(cron.tab.auth$`Normative sample` < .65), 4])
  min.factors <- paste(min.factors, " (", min.values, "), ", sep = "", collapse = "")
  
  kable(cron.tab.auth[1:21, ], format = "latex", digits = 2, booktabs = T, row.names = F,
        caption = "Alpha Cronbach - Authors' research on normative sample (n=1340)",
        align = c("l", "r", "r", "r"), label = "authorCronbach1")
  kable(cron.tab.auth[22:35, ], format = "latex", digits = 2, booktabs = T, row.names = F,
        caption = "Alpha Cronbach - Authors' research on normative sample (n=1340)",
        align = c("l", "r", "r", "r"), label = "authorCronbach2")
```
It can be noted that, from the authors' research, the minimum value of the Cronbach \(\alpha\) coefficient was `r min.norm`, and the maximum value was `r max.norm`, both values being obtained on the normative sample.The factors with low values of internal consistency and which pose problems regarding the reliability of the measurement are: *`r min.factors`*.

## Procedure
The analysis will involve the initial study of the internal consistency, for each scale, using the \(\alpha\) Cronbach [@Cronbach-1951] in order to calculate the internal consistency coefficient \(\alpha\) (Guttman \(\lambda\)~3~), then comparing the coefficients with the values reported by authors [@BigFive-plus].

We will then test the model in which the latent trait loads the 8 indicators, for each of the 6 facets of a dimension, and the existence of the common dimension for all 6 latent factors. After interpreting the parameters and diagnosing the models, they will be re-specified, identifying, if necessary, better explanatory models.

**In the first phase** we will present the comparative analysis of the authors regarding the internal consistency using the **alpha Cronbach method of \(\tau\)-equivalent reliability** [@Cronbach-1951], including both global indicators and those broken down by *gender* and *method of data gathering (pencil-paper or online)*. The analysis eas performed using the **psych** package [@R-psych], starting from the condition of the cumulative items, the total score resulting from summing the score of the 8 items (8 point of theoretical range), with identifying the items' negative variance and automatically recording. A non-parametric re-sampling was also used, simulating 100 samples in order to verify the stability of the parameters.

**In the second phase**, the Big Five Plus Inventory analysis will be performed according to a classical model of confirmatory factor analysis with uncorrelated second order factors, which will be analyzed using the **lavaan** package.[@R-lavaan]. Since the indicators are dichotomous, we will use the *method of estimating the thresholds of the response categories* in which each indicator becomes loaded in the latent trait and determines an active response (1-Yes) if it exceeds its threshold value, established by the item's position on the latent continuum. As an estimator, we will compute one from the categories of methods based on the least squares, namely **WLSM"**, which uses only the diagonal of the weighted matrix "W" (**DWLS**) and, for statistical tests, adjusted means. The "Satorra Bentler" version of the \(\chi\)^2^ test was used to test the overall fit, adjusting the means. [@Skrondal-2005].

## Data analysis
All analyzes were performed using: `r cite_r("r-references.bib")`

# Results
## Scales' reliability


## Data screening and descriptive statistics


## Confirmatory Factor Analisys


### Extraversion
```{r sem-extra, echo=F, include=F}
  source("04 - CFA - Extraversion.R")
  # Analiza modelului global
  nr.param <- as.numeric(extraversion.ini$FIT["npar"])
  df <- as.numeric(extraversion.ini$FIT["df.scaled"])
  chi.sq <- as.numeric(extraversion.ini$FIT["chisq.scaled"])
  p.val <- as.numeric(extraversion.ini$FIT["pvalue.scaled"])
  rmsea <- as.numeric(extraversion.ini$FIT["rmsea"])
  rmsea.p <- as.numeric(extraversion.ini$FIT["rmsea.pvalue"])
  rmsea.ci.lo <- as.numeric(extraversion.ini$FIT["rmsea.ci.lower"])
  rmsea.ci.hi <- as.numeric(extraversion.ini$FIT["rmsea.ci.upper"])
  tli <- as.numeric(extraversion.ini$FIT["tli.scaled"])
  srmr <- as.numeric(extraversion.ini$FIT["srmr"])
  
  # Analiza parametrilor - Factorul cel mai puternic incarcat
  b_high <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Extraversion" & extraversion.ini$PE$rhs == "Gregariousness" & extraversion.ini$PE$op == "=~"), 5]
  beta_high <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Extraversion" & extraversion.ini$PE$rhs == "Gregariousness" & extraversion.ini$PE$op == "=~"), 11]
  r_high <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Gregariousness" & extraversion.ini$PE$op == "r2"), 5]
  
  # Analiza parametrilor - Factorul cel mai slab incarcat
  b_low <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Extraversion" & extraversion.ini$PE$rhs == "Excitement" & extraversion.ini$PE$op == "=~"), 5]
  beta_low <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Extraversion" & extraversion.ini$PE$rhs == "Excitement" & extraversion.ini$PE$op == "=~"), 11]
  r_low <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "Excitement" & extraversion.ini$PE$op == "r2"), 5]
  
  # Analiza itemilor problematici
  I7.N <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I7" & extraversion.ini$PE$op == "r2"), 3]
  I7.R <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I7" & extraversion.ini$PE$op == "r2"), 5]
  I7.B <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I7" & extraversion.ini$PE$op == "=~"), 5]
  I7.Beta <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I7" & extraversion.ini$PE$op == "=~"), 11]
  
  I28.N <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I28" & extraversion.ini$PE$op == "r2"), 3]
  I28.R <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I28" & extraversion.ini$PE$op == "r2"), 5]
  I28.B <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I28" & extraversion.ini$PE$op == "=~"), 5]
  I28.Beta <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I28" & extraversion.ini$PE$op == "=~"), 11]
  
  I31.N <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I31" & extraversion.ini$PE$op == "r2"), 3]
  I31.R <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I31" & extraversion.ini$PE$op == "r2"), 5]
  I31.B <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I31" & extraversion.ini$PE$op == "=~"), 5]
  I31.Beta <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I31" & extraversion.ini$PE$op == "=~"), 11]
  
  I37.N <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I37" & extraversion.ini$PE$op == "r2"), 3]
  I37.R <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I37" & extraversion.ini$PE$op == "r2"), 5]
  I37.B <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I37" & extraversion.ini$PE$op == "=~"), 5]
  I37.Beta <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I37" & extraversion.ini$PE$op == "=~"), 11]
  
  I30.N <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I30" & extraversion.ini$PE$op == "r2"), 3]
  I30.R <- extraversion.ini$PE[which(extraversion.ini$PE$lhs == "I30" & extraversion.ini$PE$op == "r2"), 5]
  I30.B <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I30" & extraversion.ini$PE$op == "=~"), 5]
  I30.Beta <- extraversion.ini$PE[which(extraversion.ini$PE$rhs == "I30" & extraversion.ini$PE$op == "=~"), 11]
  
  # Analiza modelului respecificat
  r.df <- as.numeric(extraversion.r$FIT["df.scaled"])
  r.chi.sq <- as.numeric(extraversion.r$FIT["chisq.scaled"])
  r.p.val <- as.numeric(extraversion.r$FIT["pvalue.scaled"])
  r.rmsea <- as.numeric(extraversion.r$FIT["rmsea"])
  r.rmsea.p <- as.numeric(extraversion.r$FIT["rmsea.pvalue"])
  r.rmsea.ci.lo <- as.numeric(extraversion.r$FIT["rmsea.ci.lower"])
  r.rmsea.ci.hi <- as.numeric(extraversion.r$FIT["rmsea.ci.upper"])
  r.tli <- as.numeric(extraversion.r$FIT["tli.scaled"])
  r.srmr <- as.numeric(extraversion.r$FIT["srmr"])
```
Varianța celor 48 de itemi dihotomici explicată de cei 6 factori latenți a căror varianță, mai apoi, va fi explicată de un factor de ordin doi, mai exact de **dimensiunea Extraversiune**, în urma analizei a generat o soluție stabilă după 29 de iterații, estimându-se un număr `r nr.param` parametri liberi, pentru o estimare validă fiind necesare minimum `r nr.param * 10` observații, ideal `r nr.param * 20` observații, condiția volumului lotului de cercetare fiind îndeplinită.

Modelul global cu un singur factor latent de ordin doi nu este însă susținut în mod corespunzător de date *(Robust \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`)*, testul de potrivire a modelului eșuând și respingându-se ipoteza nulă **H~0~:** *Nu există nicio discrepanță statistic semnificativă între covarianțele stipulate la nivelul populației și covarianțele estimate de model.* Erorile de aproximare sunt însă acceptabile *(RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`)*, chiar dacă ipoteza nulă de potrivire **H~0~:** *Reziduurile standardizate dintre covarianțele rezultate din date și matricea ipotetică de covarianțe sunt nule* este respinsă, valoarea arătând eșecul testul de nepotrivire (\(\epsilon\)>.10) și reziduuri standardizate statistic semnificative între covarianțele rezultate din date și matricea ipotetică de covarianțe.

Indicele Tucker-Lewis de comparare cu modelul de bază *(Robust TLI=`r tli`, SRMR=`r srmr`)* arată că modelul se îmbunătățește cu `r tli * 100`% în comparație cu modelul nul, în condițiile în care indicatorul standardizat al reziduurilor are o valoare ușor ridicată.

Din cauza unei probleme de identificare empirică și care a generat o matrice neinversabilă, erorile standard ale estimării parametrilor nu au putut fi calculate, prin urmare nici testele statistice, așadar parametrii vor fi apreciați pe baza valorilor nestandardizate și standardizate.

**Extraversiunea**, ca factor latent de ordin doi, încarcă cel mai puternic factorul latent *Sociabilitate* (B=`r b_high`, \(\beta\)=`r beta_high`, R^2^=`r r_high`) și cel mai slab factorul latent *Excitabilitate* (B=`r b_low`, \(\beta\)=`r beta_low`, R^2^=`r r_low`), valorile varianței explicate și ale coeficientului de încărcare sugerând, de fapt, că *Excitabilitatea* nu reprezintă o fațetă a extraversiunii, cu atât mai mult cu cât cei 8 itemi sunt încărcați foarte bine de aceasta.

```{r EXT-Loading, results='asis'}
  apa_table(load.tbl.1, row.names = F, caption = "Loadings for Friendliness' latent trait")
  apa_table(load.tbl.2, row.names = F, caption = "Loadings for Gregariousness' latent trait")
  apa_table(load.tbl.3, row.names = F, caption = "Loadings for Assertiveness' latent trait")
  apa_table(load.tbl.4, row.names = F, caption = "Loadings for Activity's latent trait")
  apa_table(load.tbl.5, row.names = F, caption = "Loadings for Excitement's latent trait")
  apa_table(load.tbl.6, row.names = F, caption = "Loadings for Cheerfulness' latent trait")
```
În privința itemilor problematici, remarcăm itemul **`r I7.N`** încărcat foarte slab de factorul **Asertivitate** (B=`r I7.B`, \(\beta\)=`r I7.Beta`, R^2^=`r I7.R`), itemii **`r I28.N`, `r I31.N` și `r I37.N`** încărcați foarte slab de factorul **Activitate** (Itemul 28: B=`r I28.B`, \(\beta\)=`r I28.Beta`, R^2^=`r I28.R`, Itemul 31: B=`r I31.B`, \(\beta\)=`r I31.Beta`, R^2^=`r I31.R` și Itemul 37: B=`r I37.B`, \(\beta\)=`r I37.Beta`, R^2^=`r I37.R`), precum și itemul **`r I30.N`** încărcat foarte slab de factorul **Veselie** (B=`r I30.B`, \(\beta\)=`r I30.Beta`, R^2^=`r I30.R`)

Respecificând modelul prin eliminarea itemilor problematici și a factorului latent *Excitabilitate*, obținem o îmbunătățire a modelului în ce privește potrivirea globală (\(\chi\)^2^~(`r r.df`)~=`r r.chi.sq`, p=`r r.p.val`,  RMSEA=`r r.rmsea`, p=`r r.rmsea.p`, CI~90%~=`r r.rmsea.ci.lo` - `r r.rmsea.ci.hi` față de \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`,  RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`), însă noul model tot nu este susținut în mod corespunzător de datele observate.

Singurul aspect remarcabil îl reprezintă creșterea capacității explicative față de modelul nul la `r r.tli * 100`% (TLI=`r r.tli`, SRMR=`r r.srmr`) față de modelul inițial cu `r tli * 100`% (TLI=`r tli`, SRMR=`r srmr`).

### Neuroticism
```{r sem-neuro, echo=F, include=F}
  source("05 - CFA - Neuroticism.R")
  # Analiza modelului global
  nr.param <- as.numeric(nevro.ini$FIT["npar"])
  df <- as.numeric(nevro.ini$FIT["df.scaled"])
  chi.sq <- as.numeric(nevro.ini$FIT["chisq.scaled"])
  p.val <- as.numeric(nevro.ini$FIT["pvalue.scaled"])
  rmsea <- as.numeric(nevro.ini$FIT["rmsea"])
  rmsea.p <- as.numeric(nevro.ini$FIT["rmsea.pvalue"])
  rmsea.ci.lo <- as.numeric(nevro.ini$FIT["rmsea.ci.lower"])
  rmsea.ci.hi <- as.numeric(nevro.ini$FIT["rmsea.ci.upper"])
  tli <- as.numeric(nevro.ini$FIT["tli.scaled"])
  srmr <- as.numeric(nevro.ini$FIT["srmr"])
  
  # Analiza parametrilor - Factorul cel mai puternic incarcat
  b_high <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Nevrozism" & nevro.ini$PE$rhs == "Anxietate" & nevro.ini$PE$op == "=~"), 5]
  beta_high <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Nevrozism" & nevro.ini$PE$rhs == "Anxietate" & nevro.ini$PE$op == "=~"), 11]
  r_high <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Anxietate" & nevro.ini$PE$op == "r2"), 5]
  
  # Analiza parametrilor - Factorul cel mai slab incarcat
  b_low <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Nevrozism" & nevro.ini$PE$rhs == "Exagerare" & nevro.ini$PE$op == "=~"), 5]
  beta_low <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Nevrozism" & nevro.ini$PE$rhs == "Exagerare" & nevro.ini$PE$op == "=~"), 11]
  r_low <- nevro.ini$PE[which(nevro.ini$PE$lhs == "Exagerare" & nevro.ini$PE$op == "r2"), 5]
  
  # Analiza itemilor problematici
  I109.N <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I109" & nevro.ini$PE$op == "r2"), 3]
  I109.R <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I109" & nevro.ini$PE$op == "r2"), 5]
  I109.B <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I109" & nevro.ini$PE$op == "=~"), 5]
  I109.Beta <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I109" & nevro.ini$PE$op == "=~"), 11]
  
  I110.N <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I110" & nevro.ini$PE$op == "r2"), 3]
  I110.R <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I110" & nevro.ini$PE$op == "r2"), 5]
  I110.B <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I110" & nevro.ini$PE$op == "=~"), 5]
  I110.Beta <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I110" & nevro.ini$PE$op == "=~"), 11]
  
  I111.N <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I111" & nevro.ini$PE$op == "r2"), 3]
  I111.R <- nevro.ini$PE[which(nevro.ini$PE$lhs == "I111" & nevro.ini$PE$op == "r2"), 5]
  I111.B <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I111" & nevro.ini$PE$op == "=~"), 5]
  I111.Beta <- nevro.ini$PE[which(nevro.ini$PE$rhs == "I111" & nevro.ini$PE$op == "=~"), 11]
```
În cazul dimensiunii Nevrozism, analiza a generat o soluție stabilă în 48 de iterații. Au fost estimați un număr de `r nr.param` parametri liberi. Pentru o estimare validă, ar fi necesar un număr minim de `r nr.param * 10` cazuri și ideal un număr de `r nr.param * 20` cazuri, astfel că putem considera îndeplinită această condiție. 
Ca și în cazul dimensiunii Extraversiune, modelul nu este susținut în mod corespunzător de date,*Robust \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`*. Cu toate acestea, erorile de aproximare sunt acceptabile *RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`*, iar indicele Tucker-Lewis de comparare cu modelul de bază *Robust TLI=`r tli`* arată că modelul se îmbunătățește cu `r tli * 100`% în comparație cu modelul nul. Indicatorul standardizat al reziduurilor are o valoare acceptabilă, SRMR = `r srmr`.

Factorul latent cel mai puternic încărcat de Nevrozism este **Anxietatea** (B=`r b_high`, \(\beta\)=`r beta_high`, R^2^=`r r_high`), în timp ce factorul cel mai slab încărcat este **Exagerarea** (B=`r b_low`, \(\beta\)=`r beta_low`, R^2^=`r r_low`), analizele indicând că aceasta nu reprezintă o fațetă reprezentativă a Nevrozismului.

În privința itemilor problematici, remarcăm itemul **`r I109.N`** încărcat  slab de factorul **Timiditate** (B=`r I109.B`, \(\beta\)=`r I109.Beta`, R^2^=`r I109.R`), itemul **`r I110.N`** încărcat slab de factorul **Exagerare** (B=`r I110.B`, \(\beta\)=`r I110.Beta`, R^2^=`r I110.R`), precum și itemul **`r I111.N`** încărcat  slab de factorul **Vulnerabilitate** (B=`r I111.B`, \(\beta\)=`r I111.Beta`, R^2^=`r I111.R`)

### Agreabilitate
```{r sem-agrea, echo=F, include=F}
  source("06 - CFA - Agreabilitate.R")
  df <- as.numeric(Agreab.ini$FIT["df.scaled"])
  chi.sq <- as.numeric(Agreab.ini$FIT["chisq.scaled"])
  p.val <- as.numeric(Agreab.ini$FIT["pvalue.scaled"])
  rmsea <- as.numeric(Agreab.ini$FIT["rmsea"])
  rmsea.p <- as.numeric(Agreab.ini$FIT["rmsea.pvalue"])
  rmsea.ci.lo <- as.numeric(Agreab.ini$FIT["rmsea.ci.lower"])
  rmsea.ci.hi <- as.numeric(Agreab.ini$FIT["rmsea.ci.upper"])
  tli <- as.numeric(Agreab.ini$FIT["tli.scaled"])
  srmr <- as.numeric(Agreab.ini$FIT["srmr"])
  
  # Analiza parametrilor - Factorul cel mai puternic incarcat
  b_high <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Agreabilitate" & Agreab.ini$PE$rhs == "Altruism" & Agreab.ini$PE$op == "=~"), 5]
  beta_high <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Agreabilitate" & Agreab.ini$PE$rhs == "Altruism" & Agreab.ini$PE$op == "=~"), 11]
  r_high <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Altruism" & Agreab.ini$PE$op == "r2"), 5]
  
  # Analiza parametrilor - Factorul cel mai slab incarcat
  b_low <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Agreabilitate" & Agreab.ini$PE$rhs == "Modestie" & Agreab.ini$PE$op == "=~"), 5]
  beta_low <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Agreabilitate" & Agreab.ini$PE$rhs == "Modestie" & Agreab.ini$PE$op == "=~"), 11]
  r_low <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "Modestie" & Agreab.ini$PE$op == "r2"), 5]
  
    # Analiza itemilor problematici
  I89.N <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "I89" & Agreab.ini$PE$op == "r2"), 3]
  I89.R <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "I89" & Agreab.ini$PE$op == "r2"), 5]
  I89.B <- Agreab.ini$PE[which(Agreab.ini$PE$rhs == "I89" & Agreab.ini$PE$op == "=~"), 5]
  I89.Beta <- Agreab.ini$PE[which(Agreab.ini$PE$rhs == "I89" & Agreab.ini$PE$op == "=~"), 11]
  
  I79.N <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "I79" & Agreab.ini$PE$op == "r2"), 3]
  I79.R <- Agreab.ini$PE[which(Agreab.ini$PE$lhs == "I79" & Agreab.ini$PE$op == "r2"), 5]
  I79.B <- Agreab.ini$PE[which(Agreab.ini$PE$rhs == "I79" & Agreab.ini$PE$op == "=~"), 5]
  I79.Beta <- Agreab.ini$PE[which(Agreab.ini$PE$rhs == "I79" & Agreab.ini$PE$op == "=~"), 11]
```

Pentru meta-factorul Agreabilitate, analiza a generat o soluție stabilă în 29 de iterații. 

Rezultatele arată că modelul nu este susținut în mod corespunzător de date,*Robust \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`*, *RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`*, *Robust TLI=`r tli`*. Modelul se îmbunătățește cu doar `r tli * 100`% în comparație cu modelul nul. Indicatorul standardizat al reziduurilor are o valoare pest pragul acceptabil, SRMR = `r srmr`.

Factorul latent cel mai puternic încărcat de Agreabilitate este **Altruismul** (B=`r b_high`, \(\beta\)=`r beta_high`, R^2^=`r r_high`), în timp ce factorul cel mai slab încărcat este **Modestia** (B=`r b_low`, \(\beta\)=`r beta_low`, R^2^=`r r_low`).

În privința itemilor problematici, observăm faptul că itemul **`r I89.N`** este încărcat  slab de factorul **Moralitate** (B=`r I89.B`, \(\beta\)=`r I89.Beta`, R^2^=`r I89.R`), iar itemul **`r I79.N`**  este încărcat slab de factorul **Modestie** (B=`r I79.B`, \(\beta\)=`r I79.Beta`, R^2^=`r I79.R`).

### Constiinciozitate
```{r sem-const, echo=F, include=F}
  source("07 - CFA - Constiinciozitate.R")
  df <- as.numeric(Const.ini$FIT["df.scaled"])
  chi.sq <- as.numeric(Const.ini$FIT["chisq.scaled"])
  p.val <- as.numeric(Const.ini$FIT["pvalue.scaled"])
  rmsea <- as.numeric(Const.ini$FIT["rmsea"])
  rmsea.p <- as.numeric(Const.ini$FIT["rmsea.pvalue"])
  rmsea.ci.lo <- as.numeric(Const.ini$FIT["rmsea.ci.lower"])
  rmsea.ci.hi <- as.numeric(Const.ini$FIT["rmsea.ci.upper"])
  tli <- as.numeric(Const.ini$FIT["tli.scaled"])
  srmr <- as.numeric(Const.ini$FIT["srmr"])
  
  # Analiza parametrilor - Factorul cel mai puternic incarcat
  b_high <- Const.ini$PE[which(Const.ini$PE$lhs == "Constiinciozitate" & Const.ini$PE$rhs == "Perseverenta" & Const.ini$PE$op == "=~"), 5]
  beta_high <- Const.ini$PE[which(Const.ini$PE$lhs == "Constiinciozitate" & Const.ini$PE$rhs == "Perseverenta" & Const.ini$PE$op == "=~"), 11]
  r_high <- Const.ini$PE[which(Const.ini$PE$lhs == "Perseverenta" & Const.ini$PE$op == "r2"), 5]
  
  # Analiza parametrilor - Factorul cel mai slab incarcat
  b_low <- Const.ini$PE[which(Const.ini$PE$lhs == "Constiinciozitate" & Const.ini$PE$rhs == "Prudenta" & Const.ini$PE$op == "=~"), 5]
  beta_low <- Const.ini$PE[which(Const.ini$PE$lhs == "Constiinciozitate" & Const.ini$PE$rhs == "Prudenta" & Const.ini$PE$op == "=~"), 11]
  r_low <- Const.ini$PE[which(Agreab.ini$PE$lhs == "Prudenta" & Const.ini$PE$op == "r2"), 5]
  
    # Analiza itemilor problematici
  I147.N <- Const.ini$PE[which(Const.ini$PE$lhs == "I147" & Const.ini$PE$op == "r2"), 3]
  I147.R <- Const.ini$PE[which(Const.ini$PE$lhs == "I147" & Const.ini$PE$op == "r2"), 5]
  I147.B <- Const.ini$PE[which(Const.ini$PE$rhs == "I147" & Const.ini$PE$op == "=~"), 5]
  I147.Beta <- Const.ini$PE[which(Const.ini$PE$rhs == "I147" & Const.ini$PE$op == "=~"), 11]
  
  I172.N <- Const.ini$PE[which(Const.ini$PE$lhs == "I172" & Const.ini$PE$op == "r2"), 3]
  I172.R <- Const.ini$PE[which(Const.ini$PE$lhs == "I172" & Const.ini$PE$op == "r2"), 5]
  I172.B <- Const.ini$PE[which(Const.ini$PE$rhs == "I172" & Const.ini$PE$op == "=~"), 5]
  I172.Beta <- Const.ini$PE[which(Const.ini$PE$rhs == "I172" & Const.ini$PE$op == "=~"), 11]

  I174.N <- Const.ini$PE[which(Const.ini$PE$lhs == "I174" & Const.ini$PE$op == "r2"), 3]
  I174.R <- Const.ini$PE[which(Const.ini$PE$lhs == "I174" & Const.ini$PE$op == "r2"), 5]
  I174.B <- Const.ini$PE[which(Const.ini$PE$rhs == "I174" & Const.ini$PE$op == "=~"), 5]
  I174.Beta <- Const.ini$PE[which(Const.ini$PE$rhs == "I174" & Const.ini$PE$op == "=~"), 11]
```

Pentru meta-factorul Conștiinciozitate, analiza a generat o soluție stabilă în 29 de iterații. 

Rezultatele arată că modelul nu este susținut în mod corespunzător de date,*Robust \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`*, *RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`*, *Robust TLI=`r tli`*. Modelul se îmbunătățește cu  `r tli * 100`% în comparație cu modelul nul. Indicatorul standardizat al reziduurilor are o valoare pest pragul acceptabil, SRMR = `r srmr`.

Factorul latent cel mai puternic încărcat de Conștiinciozitate este **Perseverența** (B=`r b_high`, \(\beta\)=`r beta_high`, R^2^=`r r_high`), în timp ce factorul cel mai slab încărcat este **Prudența** (B=`r b_low`, \(\beta\)=`r beta_low`, R^2^=`r r_low`).

În privința itemilor problematici, observăm faptul că itemul **`r I147.N`** este încărcat  slab de factorul **Datorie** (B=`r I147.B`, \(\beta\)=`r I147.Beta`, R^2^=`r I147.R`), itemul **`r I172.N`**  este încărcat slab de factorul **Ambiție** (B=`r I79.B`, \(\beta\)=`r I79.Beta`, R^2^=`r I79.R`), iar itemul **`r I174.N`** încărcat  slab de factorul **Prudență** (B=`r I174.B`, \(\beta\)=`r I174.Beta`, R^2^=`r I174.R`).

### Deschidere
```{r sem-open, echo=F, include=F}
  source("08 - CFA - Deschidere.R")
  df <- as.numeric(Deschidere.ini$FIT["df.scaled"])
  chi.sq <- as.numeric(Deschidere.ini$FIT["chisq.scaled"])
  p.val <- as.numeric(Deschidere.ini$FIT["pvalue.scaled"])
  rmsea <- as.numeric(Deschidere.ini$FIT["rmsea"])
  rmsea.p <- as.numeric(Deschidere.ini$FIT["rmsea.pvalue"])
  rmsea.ci.lo <- as.numeric(Deschidere.ini$FIT["rmsea.ci.lower"])
  rmsea.ci.hi <- as.numeric(Deschidere.ini$FIT["rmsea.ci.upper"])
  tli <- as.numeric(Deschidere.ini$FIT["tli.scaled"])
  srmr <- as.numeric(Deschidere.ini$FIT["srmr"])
  
  # Analiza parametrilor - Factorul cel mai puternic incarcat
  b_high <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "Deschidere" & Deschidere.ini$PE$rhs == "Imaginatie" & Deschidere.ini$PE$op == "=~"), 5]
  beta_high <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "Deschidere" & Deschidere.ini$PE$rhs == "Imaginatie" & Deschidere.ini$PE$op == "=~"), 11]
  r_high <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "Imaginatie" & Deschidere.ini$PE$op == "r2"), 5]
  
  # Analiza parametrilor - Factorul cel mai slab incarcat
  b_low <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "Deschidere" & Deschidere.ini$PE$rhs == "Emotionalitate" & Deschidere.ini$PE$op == "=~"), 5]
  beta_low <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "Deschidere" & Deschidere.ini$PE$rhs == "Emotionalitate" & Deschidere.ini$PE$op == "=~"), 11]
  r_low <- Deschidere.ini$PE[which(Agreab.ini$PE$lhs == "Emotionalitate" & Deschidere.ini$PE$op == "r2"), 5]
  
    # Analiza itemilor problematici
  I195.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I195" & Deschidere.ini$PE$op == "r2"), 3]
  I195.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I195" & Deschidere.ini$PE$op == "r2"), 5]
  I195.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I195" & Deschidere.ini$PE$op == "=~"), 5]
  I195.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I195" & Deschidere.ini$PE$op == "=~"), 11]
  
  I221.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I221" & Deschidere.ini$PE$op == "r2"), 3]
  I221.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I221" & Deschidere.ini$PE$op == "r2"), 5]
  I221.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I221" & Deschidere.ini$PE$op == "=~"), 5]
  I221.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I221" & Deschidere.ini$PE$op == "=~"), 11]

  I230.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I230" & Deschidere.ini$PE$op == "r2"), 3]
  I230.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I230" & Deschidere.ini$PE$op == "r2"), 5]
  I230.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I230" & Deschidere.ini$PE$op == "=~"), 5]
  I230.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I230" & Deschidere.ini$PE$op == "=~"), 11]

  I207.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I207" & Deschidere.ini$PE$op == "r2"), 3]
  I207.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I207" & Deschidere.ini$PE$op == "r2"), 5]
  I207.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I207" & Deschidere.ini$PE$op == "=~"), 5]
  I207.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I207" & Deschidere.ini$PE$op == "=~"), 11]

  I216.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I216" & Deschidere.ini$PE$op == "r2"), 3]
  I216.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I216" & Deschidere.ini$PE$op == "r2"), 5]
  I216.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I216" & Deschidere.ini$PE$op == "=~"), 5]
  I216.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I216" & Deschidere.ini$PE$op == "=~"), 11]

  I238.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I238" & Deschidere.ini$PE$op == "r2"), 3]
  I238.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I238" & Deschidere.ini$PE$op == "r2"), 5]
  I238.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I238" & Deschidere.ini$PE$op == "=~"), 5]
  I238.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I238" & Deschidere.ini$PE$op == "=~"), 11]

  I240.N <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I240" & Deschidere.ini$PE$op == "r2"), 3]
  I240.R <- Deschidere.ini$PE[which(Deschidere.ini$PE$lhs == "I240" & Deschidere.ini$PE$op == "r2"), 5]
  I240.B <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I240" & Deschidere.ini$PE$op == "=~"), 5]
  I240.Beta <- Deschidere.ini$PE[which(Deschidere.ini$PE$rhs == "I240" & Deschidere.ini$PE$op == "=~"), 11]
```

În ceea ce privește meta-factorul Deschidere, analiza a ajuns la o soluție validă în 29 de iterații. 

Din nou, rezultatele arată că modelul nu este susținut în mod corespunzător de date,*Robust \(\chi\)^2^~(`r df`)~=`r chi.sq`, p=`r p.val`*, *RMSEA=`r rmsea`, p=`r rmsea.p`, CI~90%~=`r rmsea.ci.lo` - `r rmsea.ci.hi`*, *Robust TLI=`r tli`*, *SRMR = `r srmr`*.

Factorul latent cel mai puternic încărcat de Deschidere este **Imaginația** (B=`r b_high`, \(\beta\)=`r beta_high`, R^2^=`r r_high`), în timp ce factorul cel mai slab încărcat este **Emoționalitatea** (B=`r b_low`, \(\beta\)=`r beta_low`, R^2^=`r r_low`).

În privința itemilor problematici, observăm faptul că itemul **`r I195.N`** este încărcat  slab de factorul **Emoționalitate** (B=`r I147.B`, \(\beta\)=`r I147.Beta`, R^2^=`r I147.R`). În cazul factorului **Liberalism**, mai mulți itemi sunt problematici: itemul **`r I207.N`** (B=`r I207.B`, \(\beta\)=`r I207.Beta`, R^2^=`r I207.R`),itemul **`r I216.N`** (B=`r I216.B`, \(\beta\)=`r I216.Beta`, R^2^=`r I216.R`), itemul **`r I238.N`**  (B=`r I238.B`, \(\beta\)=`r I238.Beta`, R^2^=`r I238.R`), precum și itemul **`r I240.N`** (B=`r I240.B`, \(\beta\)=`r I240.Beta`, R^2^=`r I240.R`). Itemul **`r I221.N`** (B=`r I221.B`, \(\beta\)=`r I221.Beta`, R^2^=`r I221.R`), precum și itemul **`r I230.N`** (B=`r I230.B`, \(\beta\)=`r I230.Beta`, R^2^=`r I240.R`) sunt încărcați slab de factorul Intelect.


# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
